\Review{12-18-98}{Madison Oyster Bar, South Bend, IN, USA}{JAJ\char`_JAJ}{Though we don't have a setlist for this show (it was accidentally deleted from the original UM setlist file years ago), I remember specifically seeing the boys at MOB on the Friday night after finals at ND, fall semester 1998.  A nice pre-party with some friends off campus made for a very fun night at good ol' MOB.}
\Review{10-06-00}{Park West, Chicago, IL, USA}{jcforst}{This was the first of over a hundred shows attended personally, it's easy to say i was sold right away.  I can still picture Bayliss in his hoodie and Jake with his stash.  Now looking back, i must say it was hearing Divisions and Front Porch in the first set that really must have grabbed me.  Their cover of Fool in the Rain was the icing on the cake, especially when it was reprised for the final song.   The Park West was a perfect place to catch these guys for the first time seeing that it still holds a special place in the hearts of the band and the phreaks.  I look to this day quite often while listening to Umphrey's for it led me on a journey that eventually took me to Europe, my first cruise and my first show at Red Rocks.  Even though Jake was reasonably new as a full time member, you could see the magic on stage.  Thanks Fellas!}
\Review{10-20-00}{The Canopy Club, Urbana, IL, USA}{McLSucks}{On this, the 12th anniversary of my first show, I thought I'd share what little I remember about it. They had been hyped up to me by a few friends, including one who'd been seeing them at Notre Dame since the start.  they were really talented...I couldn't tell when one song ended and the next one began.  The Hair Band Medley was *AWFUL*. There was some random girl on-stage singing a song or two, and the band clearly regretted that decision.   but really, my strongest memories about this show don't stem from the music, but my impressions of the band and organization, and how seriously they take the music.  leaving the show, I wasn't sure to think. I taped the show (no idea where the tape actually wound up), and when I went to retrieve my deck, KB told me to throw the tape away or tape over it...that the show was terrible. Vince, an acquaintance of my friend who encouraged me to attend the show, also said something similar, he apologized for a poor show. Weird, right?  I didn't think it was that bad...I was entertained and impressed enough to give them another shot at some point (and living in Illinois, those were rather frequent)  The following week, I met Brendan at a Disco Biscuits show in Chicago. He was informed that this had been my first show. He profusely apologized, declaring that I shouldn't judge the band based upon that performance, and hoped I would give them another shot.   Fast-forward 3 years later, a show at the Canopy, I bring up how this was my first show to Pony, sure enough, he had a vivid memory of the show was and expressed shock that I ever returned.   12 years later...they're going strong as ever, playing as consistently as they ever have at any point in their career. So glad I was able to overcome a poor first impression of the music (but a great first impression of everyone involved)  strangely, the All Things Ninja from this show made it onto One Fat Sucka.}
\Review{10-24-01}{Cicero's, St. Louis, MO, USA}{mittens}{My First show...... I had seen some Umphrey's tapes on some tape trees and decided to check them out while I was living in St. Louis.  Anyone who's been to Cicero's knows how small the venue is, 250 max.  There were probably less than 50 people there.  I remember seeing the band hanging out among the crowd and hoped they were making ends meet so they could keep playing live because they put on one of the most inspired performances I've ever seen from a band.  Looking back, it's a fantasy setlist. If Nachos for Two isn't enough to prove it, how about My favorite Things.  Sick show from an unbelievable Oct. 2001 tour.}
\Review{06-21-02}{Bonnaroo Music \& Arts Festival, Manchester, TN, USA}{StellaBlueEcho}{1st show as well and have enjoyed every moment since then. So many people at this tent dancing their asses off in the unforgiving heat that day. Best band around. They were great at what they did back then and just keep getting better. Thank you for all the memories past, present, and future.}
\Review{12-14-02}{Mississippi Nights, St. Louis, MO, USA}{mittens}{Mirro's last night of tour brought the goods.  I'm not sure if this show is on people's radar but it is straight fire.    My favorite Example One of all time. This has to be one of the best encores of all time in a note perfect Fifth of Beethoven and then Last Call.}
\Review{02-04-03}{Gerstle's, Louisville, KY, USA}{McLSucks}{A Minnesota Vikings bar in Louisville, KY on a Tuesday night. Even back in 2003, one of those instances where you knew the band could kick back and be loose. The opening "DCI jam" (which was meant to poke fun at the DCI instructional videos that involve the musicians soloing in rounds) turned into a 14 minute monster with a glorious peak...yet further proof in the first two weeks of the Myers era that these guys weren't going to be slowing down. The riff that Jake starts 11:08...and then him and bb trade back and forth and build off of for the next 3 minutes is what St. Peter should have playing at the pearly gates...  Soul Food I was playful with a bunch of teases  The last appearance of the Thelonius Monk tune, Well You Needn't is noteworthy...another of those early jazz tunes that slowly faded into oblivion.   The Pure Imagination tease during Padgett's is pretty damn cool, but the Anchor Drops is my highlight of the second set. A lengthy, across the board, multi-sectional stewart that found its way into The Breeders' Cannonball, but then settled into a reggae groove that I still can't get out of my head, commonly referred to as "Ragamuffin." I don't know of any earlier appearances of Ragamuffin, it did pop up again on 4/1/03 (which was included in the Raw Stewage) and 4/22/03, and then again at UMBowl III during the S2 set. If you know of any other version, please let me know!  Ragamuffin sometimes you got to be a ragamuffin and a mine mine mine mine mine  stand tall/firm with two feet on the ground with two feet on the ground lord have mercy  Glory \textgreater \enspace  Snucka III encore is classic UMnanigans  other than that, fairly solid playing...but it's the intro jam, Soul Food I and Anchor Drops for which you should check out this show over at Archive.org}
\Review{03-29-03}{The Fox Theatre, Boulder, CO, USA}{McLSucks}{A historic show for so many reasons. I implore all serious Umphreaks to check this one out over at Archive.org  the show opened with a funny Get in the Van gag...they played the false start of the song...and then walked back off stage.  The 40's Theme with Jamie Janover on toy guitar has to be heard to be believed. It remains one of the most mindblowing "how the hell did they do that so well" moments. They way the band traded licks with the toy guitar is hilarious and musically impressive at the same time. This then turned into the oft repeated Zsa Zsa Gabore jam, and then a fantastic full-fledged stwart after it before returning to 40's.   The Zsa Zsa jam would make it's glorious return on 4/28/12 after many years in hibernation...but the coolest part is that they also brought back the 2nd part of the 40's stew and made it a vocal stewart.  Second set opens with a 24 minute triple wide that features a lot of patient, ambient jamming. a must hear.  The other historic aspect is the stewart out of Mulche's that features the first appearance of instrumental sections from both Ocean Billy and Wife Soup.   Push the Pig with November Rain ending was also hilarious.}
\Review{10-15-03}{Witz End, Stevens Point, WI, USA}{UWPointers}{Its been near 12 and a half years later . . . and I still listen to this show for the great lead off into a classic, gritty Phil's Farm and the intimacy of the venue.  The Witz End was a small bar/supper club in the middle of nowhere that couldn't fit more than 75 people, tops.  The show was the day AFTER the famed "Steve Bartman" game, and prior to the show a group of us UW-Pointers went early for  pre-show beers, and were fortunate enough to imbibe and visit with the band and watch the Cubs playoff game.  They were not happy about the previous day's Bartman game, and went into the show even more downtrodden due to a Cubs Game 7 loss immediately before the show began.  Yet, a fantastic and intimate show in a great, classic Wisconsin atmosphere.  Sadly, the Witz End later burned to the ground.}
\Review{12-06-03}{The Canopy Club, Urbana, IL, USA}{McLSucks}{Another one of those crazy Canopy nights...like the previous December, something must have been in the air and they busted out a unique one this evening.   The show opens with a 14 minute Mulche's, the first time it was ever given the treatment. There's not one but two worthwhile improvisational sections. I still wish that the song's improvisational future would have tailored more to this version.   Fussy \textgreater \enspace  Tomorrow Never Knows is still the best segue in the UM repertoire...when that first crash of TNK hits...straight butter.   Gotta love the XRT Xmas Medley...debuted the night before and played once more this evening. punk jingle bells \textgreater \enspace  country deck the halls \textgreater \enspace  reggae grandma got run over by a reindeer \textgreater \enspace  carol of the bells. another example of the humor, creativity and chops pervasive in UM. some pretty funny 'fuck yeah'-ing at the end, too.  A rather solid version of Water that sees jake and brendan slowly drifting away from the middle section into some great dissonant territory with Kris leading the charge behind them.  Phil's \textgreater \enspace  Glory \textgreater \enspace  Phil's \textgreater \enspace  14 min stew \textgreater \enspace  middle section of N2F \textgreater \enspace  Phil's...just listen to this one.   The rare Pork Chop Pie, 9 years later, is still a song I request over and over. Such a great carryover from the Ali Baba's Tahini oeuvre.   some silliness with Hysteria \textgreater \enspace  In Violation of Yes.  then the 26 minute Nothing Too Fancy \textgreater \enspace  Ocean Billy \textgreater \enspace  Nothing Too Fancy encore is about as strong a finish as you can get.   Listen to it on the Archive}
\Review{02-09-04}{People's, Ames, IA, USA}{taperchef}{My first um show and it was certainly memorable. Hot hot improve in SF1, a beatles cover, phils, and hendrix. Set 2 bridgeless and the Zappa encore stand out for me. I partied and talked with Jake in the basement of Peoples "Lumpys" that served as a back stage for the band.It was a fun night and turned me on to Umphreys proper.}
\Review{02-21-04}{The Funk Box, Baltimore, MD, USA}{McLSucks}{Some nights will live forever, the fourth and final night of the run with Joshua Redman will remain with me in perpetuity. Archive.org link. Well worth the effort of converting from FLAC.  First set was fairly standard, a nice subtle Kat's Tune seemed an innocuous intro after a rowdy Saturday night in NYC the night before. A reasonable Much Obliged \textgreater \enspace  Crooked couldn't really prepare for what happened next, though.  FF and the ensuing jam would contain one of those monumental pieces of improv that you chase all over the country for. It started with one of those ascending chord progressions that lends itself to a slow-building crescendo, and that's what the band delivered. A fun little Bayliss pull-off riff sets the melody and off they go. I've listened to this probably over 100 times, and it's really funny to hear that the band doesn't quite know how to play it. Jake is struggling to play the "right" notes, Brendan seems to keep slightly modifying his riff because it doesn't sound "100\% right"...but they keep plowing through, and they keep taking it higher and higher. Of course, none of that actually matters. The build itself, basking in the sound, is life-affirming. This would be attempted a couple more times (most notably on 12/3/04), but I contest that none would ever equal this one.   Rest of the set is standard fare. After that FF, everyone was looking at each other..."did you just see that?"...a shared moment that everyone was still buzzing about through setbreak.   This Joshua Redman cat, he's got a future. He had really managed to gel by this fourth night. On this evening, the band had no fear of stretching songs far beyond their boundaries and Redman was gladly along for the ride. It was difficult to contain my giddiness when World's Running Down started...it seemed clear this set was going to be different, they took off as a 7-piece unit with no looking back...then the drop into Blue Echo was unexpected and I knew it would be another opportunity for them to stretch things out...again...they did not disappoint.  All Things Ninja...it's impressive that of the songs in the UM repertoire, UM would choose this as a song option for him to learn, and he would choose to learn it. I suppose it shouldn't have been that much of a surprise after seeing how well they played Der Bluten Kat together...but still...Ninja? Yes, please.   And finally, we come to Wife Soup... This is the ultimate Wife Soup for me, featuring a Redman contribution that become referred to as The Note. If you're not familiar...I implore you to check out this show if only for The Note. Of course, I'd think you'd be ludicrous to not enjoy the rest of it...but this, again, was one of those moments...to be lucky enough to be there...The Note was like a shot of endorphins, adrenaline, dopamine...all of those chemicals your body produces that make you feel good from natural stimuli? This was that stimulus.   Unfortunately, as the second set ran long (due to the lengthy improv), the DBK encore had to be cut, but hey...Waiting Room is always a great encore/set closer.}
\Review{03-12-04}{Park West, Chicago, IL, USA}{jessek}{204-03-12 Park West, Chicago, IL  This show holds a special place in my heart as it was the first show I saw as a fan.  I had seen the band once before in 2002 but it didn't quite take. Two years later, the same lovely couple (veteran fans) hadn't given up on me and took me to this show… and it clicked.  I was already semi-familiar at this point, but seeing them live again felt completely different and ingrained an opinion that this was the best thing happening in live music.  Set I:  First set is notable because of all the mood changes.  A truly impressive ADD set that touches on nearly every style that Umphrey's plays.  I think the set lacks a bit of fluidity in return, but as a fan just learning the scope what these guys could do, it was eye opening.  We start off with a nice warm-up intro jam.  Bright Lights is standard (new), but an upbeat start.  Quick-drop into original OB beginning and things start to heat up.  [Side Note: early OB renditions show just how far Bayliss' vocal abilities have come in the last decade]  OB ventures into improv for the first time of the night with a funk jam (I Ran teases).  Trench Town Rock turns the whole mood upside down… happiness is unavoidable during this song and so was the case on this night.  Full stop before N2F spins the mood of the room yet again (I Ran teases).  There's a quick drop into Bad Poker and just as rapidly as the song appears, we drop back into a jam that could have easily spawned from the preceding N2F - a jam which knocks that country taste right out your mouth.  The dual guitars harmonize triplet riffs while Pony provides a nice theme as foundation.  The jam fills out nicely as guitars/keys adapt Pony's idea and then expand on it getting a bit more aggressive with each run through.  A small bounce-back develops about halfway through before Joel moves front and center for a C section with a mellow watery effect that winds it down.  Next, we get well played but fairly standard run of Wife Soup (small metal jam pulling riffs from Metallica's One), Mail Package and Prowler (more I Ran teases).  The later segues into the ending of OB, in which Bayliss stretches his final note to a place I've yet to hear in another version of the song; A truly wonderful end to the set.  Set II: Begins fairly standard, but the final run of songs is crafted incredibly and left me with a very positive impression walking out.  Stand-alone versions of Mulches and a new song Nemo start things off.  Next up is the quirky multi-sectioned In Violation of Yes featuring Jake on bass and Pony on Rhodes.  As a fledgling fan, I was blown away by Jake's ability to pick up another instrument and not only play well, but absolutely destroy it.  From here on out the set gains momentum, taking us on a fantastic musical journey through the end of the show.  Starting with the powerful Divisions sandwiched around the bands first unleashing of the double time Blue Echo (originally referred to as Techno Echo).  The Blue Echo contains a nice little improvisational bit that just sort of floats along eventually leading back to the final portion of Divisions.  The most memorable moment for me was All Things Ninja.  It was the first time I'd ever heard the song -- 15 minutes of wonderful dark ugliness that had me by the throat for its entirety.  A pause for band introductions before launching into the debut cover of Flock of Seagulls' I Ran which we all should have seen coming from the many teases in the first set (I missed them somehow).  The cover is performed very well, and segues perfectly into the Fancy Reprise -- yet another wonderful way to end a set.  Bridgeless Encore seemed like the bands attempt to wring every last bit of rage out of the crowd.  It worked.  A great high-energy encore.  I was obviously excited by my new-found incredible band.  I can remember the walk out to a friend's house on Orchard like it were yesterday -- and the excited conversation that ensued peppered with many "We told you so's" from the couple who brought me and had championed the band for so long.  I joined the Bort the next week and posted about how great this show was... and was immediately smacked down as a newbie over-fluffing a standard show.  Re-addressing this show years later, I can see how it lacks the improvisational jaunts that I've grown to love and also require out of any "great" UM show.  The obvious highlight being the N2F jam out of Bad Poker.  …but then again, for a first show, it was everything I needed to get me started on the obsession.  Something the jaded vets of today should keep in mind.  The stylistic variety, technical ability and musicianship displayed, and most importantly the capability to take me to the place that the run from Divisions on did… is something that has stuck with me all these years.  sbd mtx here: 2004-03-12 Park West}
\Review{06-11-04}{Bonnaroo Music \& Arts Festival, Manchester, TN, USA}{umphalex}{Ahhhhh, my first UM show!  Young and at Bonnaroo to see all my favorite jam bands!  This set of UM opened my eyes to appreciate UM as one of the top bands coming up...  When moe came on and then Michael Travis too I didnt even know what was going on, it blew my mind!  Highlights were definitely the jam in resolution which is long and tasty, along with a nothin too fancy and bright lights that has made me do 48 shows to date!  This whole set though is just pure UM energy and if you've never heard the download I would strongly suggest it!}
\Review{07-09-04}{The Odeon, Cleveland, OH, USA}{knowerofmanythings}{After I heard the news of my then favorite band was going to play one last festival(August 14 \& 15 2004) and then break up or go hiatus or whatever disturbing term they wanted to use. I was heart broken. I needed live music therapy.    In July 2004 I was working in retail music store and in the cd reel this band's album 'Round Room.'  I am pretty sure the song "Waves" was playing when a cute little blonde girl charged up to the counter and said "who choose to play this..." It was obvious it was me...I was wearing a '99 tour shirt.  I said it was me...and how may I help you.  I was direct and charming.  She demanded that I was to go to the Odeon that Friday to check out this Midwestern Irish band called Umphreys Mcgee, and that I won't regret it.   As a young knower I had high expectations.  I went to the show... and loved it.  My highlights were probably the whole show.  Ocean Billy- Duel face Melting Finger tapping  Tribute- Jaco going nuts the entire time.    Dump City\textgreater \enspace DBK-  I didn't know what going on...and my face was started to melt off in certain areas.    Second set I was even more blown away...though I was pretty clueless.    Plunger- Loved all the different sections.  Triplewide\textgreater \enspace Mail Package -visions of Zappa were floating in my head.    I remember loving "In the Kitchen," and was confused on "Last Man Swerving" but went along with it and head bobbed throughout the song.    Miss Gradenko-  I was fascinated by it.  The Encore: MO\textgreater \enspace M(O) spoke for itself.     I ended up working the next day ordering  The Police's 'Synchronicity.'  A few days later I bought the show off disclogic.com,and saw in the paper that they were coming back in November ordered the ticket \& Anchor Drops.   The More You Know.}
\Review{04-15-05}{The Canopy Club, Urbana, IL, USA}{knowerofmanythings}{"Welcome"  This was my 4th show. It was a wild show filled with samples, awesome banter, and really unique jams and fun covers. Well basically what every UM show is.  Plus, it was quite an adventure to get there to say the least.  Let's begin.   "Welcome"  After my flight got delayed multiple times a 45 minutes flight from Cleveland to Chicago ended up to be super duper stressful and if you know my concert anxiety I was a nervous wreck.I am pretty sure I could have driven to Chicago for as long as I was at the airport.   Finally I arrived Chicago.  My buddy picked me up and then it was off to Urbana.  I think it was snowed and it took forever to drive there. I was ready to rage.  As we walked in the venue Joel\& Pony started "August."  We had made itI  It was a mad house in there. It was like new years in April. People were hammered and wanted to rage. I was not too familiar with the band at this point so we watched Budney's light show for a while. Then moved to Bayliss' side, then Jake's.  The August jam was awesome.  Each section cooler than the next.    The whole first set was one seamless transition. There was a really cool wah-wah Jake led solo to made it's way into "Utopian Fir."  There were really raunchy funky jams in this version. Each section was drastically different than the next. This "Fir" I compare every  "Fir" I've ever heard to.          The "Passing" was great.  It had a graceful transition from Fir. Great segue led from the Wizard led to "Andy's Last Beer."  "Have you guy's been boozin?" BB  "This sounds really Fucked up" Jaco  "Sounds like a wash" BB   The "13 days" mixed up the rager.  This calmed down the audience. Not really.    "All right Champaign!" Kris yelled as he channeled Diamond Dave prior to "Running with the Devil."    I though what can't these guys do? and that drummer can fucking sing.  Next up was "All In Time."   People hooted and hollered.  It was a great version. Jaco went crazy.  The percussion was off the wall.  I was more than hooked.  What a first set!    Set 2.  The "Miss Tinkles Overture" started things off. Kris pounded the snare.  The dual guitar attack took off.  A great jam led by Jaco.  The first jam got weird. Then branched out and incorperated Rockwell's "Somebody's watching Me" teases.  Who does that?  It went multiple mind bending places prior to resurfacing and ending the overture.    This "Resolution" scarred me for life with the "Welcome" sample in the beginning portion of the song.     Thanks Farag!  The jams were fun.  Over all over the place.  The Wizard had a great organ solo.  They were jams that made me think about the potential of the band.      "Sociable Jimmy" had perfect placement. Bayliss altered the lyrics.  Joel had a killer Rhodes solo.    "Joel Cummins on the keys"  Bayliss mentioned it was Steve \& Bebop's birthday as well Budney's.  I think every night UM played in '05 it was Budney's birthday or at to the shows I attended or bought.  He must be as old as Joel now.    Amsterdam \& Ozzy jokes galore.    "Ozzy" led to a cool beatbox intro for "Atmosfarag."  Some how they pulled off a transition that was very 'Jim-Morrison-in-the-desert' sounding jam into "Blackwater."  Jake \& Bayliss added Badunkadunk at the end.    Kris had some great commentary after this song.  "America! Fuck yea" Kris  "You tend to bitch and moan" Jaco  I loved what they teased in "Prowler" and that led to "Glory." Jaco went ballistic.    "This next song is about getting drunk" was the intro to "Last Man Swerving" a lot of Umspeak in this one. Then Bam!  They didn't hold back at all went right into the "Dump City."  The banter is funny before "Mulche's."  The "Welcome" re appeared and then there was paradigm \& chicken banter.  Stasik was "Wastic" and started the song. The jam was intense for all intents and purposes.   The encore was "A 5th of Beethoven." Bayliss smoked a square on stage and he made fun of Joel.  It was a great way to end the show.  The 5th rocked.    And I was thought about where my 5 UM show was going to be.    The More You Know}
\Review{07-16-05}{"All Good Music Festival" Marvin's Mountaintop, Masontown, WV, USA}{smackaframalama}{first time seeing UM!!!.. also first festival!  so i had a lot of learning to do in pacing myself. to much to fast and didn't quite get what was going on with the music.  I listened to the show later and couldn't believe how amazing it was and that i was there! since then i have figured things out a little more and can balance myself to enjoy the music fully. Fortunately there would be many more shows and festivals in the future to redeem myself. Still an amazing time with my best friends, we all learned together.  Love you marvins mtn. top! and Umphreys Mcgee!}
\Review{07-23-05}{Tweeter Center for the Performing Arts, Mansfield, MA, USA}{cMags}{This was my first of (as of now) 69 shows. I first found out about UM after they did the "Molester Medley" for Halloween 2004. Phish had just broken up and I needed a new band to fill the void. I listened to the song Anchor Drops, and absolutely loved it, so I got the album for Christmas that year. This show was the first one in the NE region for that year, and it's kind of crazy to think that now, as they have played here in the winter ever since.  As soon as this show was announced, me and my buddy Rob grabbed tickets. Umphrey's, String Cheese, and Keller Williams was definitely a nice draw for us. We also wanted to see this band New Monsoon, but their set time was like 1 PM, so we said screw it.  Mulche's Odyssey featured a pause during the peaking jam to let the crowd know that KB was getting married. And they had an impromptu acapella "Kevin's Getting Married" tune. Divisions was an amazing song to see as my first "big" UM song. There wasn't any improv, just a straight stand-alone Divisions. Push The Pig had Franti come out and do some raps and stuff. Kinda cool for the 19 year old that I was at the time, but whatever. Wife Soup was a song I knew and was pumped to hear. Next was the only time I got a "I've Got A Feeling." 69 shows and still not another one haha. But I just remember being pumped to hear Bayliss nail the vocals for one of my favorite bands of all time. Finally came JaJunk which was another song I knew and was happy to hear.  All in all, it was a great introduction to a band that I would be following around for the next 7 years of my life.}
\Review{02-09-06}{First Avenue, Minneapolis, MN, USA}{xanbo}{It's no coincidence that I'm writing this immediately after watching the incredible Prince and the Revolution Live '85 limited-time stream on Youtube for a COVID-19 fundraiser. Guitarist Wendy Melvoin's first performance with Prince was right here at First Avenue in the city where The Revolution began.   You might be a little disappointed to scan the setlist and find no mention of the bloused one, but something greater began the night prior 2/8 and lasted through 2/11 - all Umphrey's original tunes without a single repeat, seemingly in response to the criticism they were a glorified cover band lacking a deep catalog. The "No Repeats No Covers ter" (in the parlance of the times) was not announced (never even officially acknowledged in any way that I'm aware of), the "cover band" slander was well known to fans, and by the end of this night in Minneapolis the opening notes of every original song became an FU to anyone who failed to consider that perhaps the real Revolution was the one we made whilst gettin' in the van.   Aside from what the other reviewer mentioned, also check out Kabump (here or any other show where it appears).   PS - releasing all four nights of this run would be a pretty swell idea.}
\Review{02-09-06}{First Avenue, Minneapolis, MN, USA}{turnerup15}{This was UM first time playing at First Ave. Before this they had only played The Cabooze on the west.   Set 1-   Tons of great energy in the room that night. Energy peaked in the first set during the Glory jam.   1st set ended with a massive Ja Junk. Deep groove from Stasik. wow.   2nd Set Notes  Bayliss guitar was not turned up loud enough in the mix so the 2x2 suffers a bit. I personally enjoy this song more when it is in the first set.     Robot World was the stand out of the whole show. Great dance untz stew with great Moog work from Joel.}
\Review{02-14-06}{Toad's Place, New Haven, CT, USA}{cMags}{This show was probably the drunkest I have ever been, and the loosest I have ever seen the band (rivaled by only the acoustic 4/5/09 show at Toad's 3 years later.) I took the Peter Pan bus down from Providence for this, and me and my buddies at Conn College got absolutely blasted for this show.  The jam in the Last Man Swerving is definitely worth checking out as the rest of the set isn't very noteworthy.  At set break, my friend got kicked out of the venue 3 separate times, but got let in again each time. He ran into Jen Hartswick at some point and went up to her and said "Will you sign my ticket stub saying 'I played with Trey?'" She looked at him and just gave him a flat out "No."   The 2nd set an encore are noteworthy for the amount of between song banter that was going on. The show was on Valentine's Day, and considering that UM show's are about 85\% men, the band was kind of poking fun that almost everyone there didn't have dates. The jam before Tinkle's had Myer's on Guitar and Brendan on Drums and was in the feel of Brendan is gay and what not. You could tell the band was just going all out cause they knew the crowd was rowdy and loose.  On tape it's not one of my favorite shows, but the experience as a hammered 20 year old single college student was one to be remembered for a lifetime.}
\Review{02-15-06}{Lupo's Heartbreak Hotel, Providence, RI, USA}{cMags}{This was the first show where I really got IT. It was a random rainy night in Providence and I remember taking the RIPTA down to Lupo's while everybody else was taking it to the Dunkin Donuts Center to watch our shitty basketball team get crushed by another Big East opponent. I went to this show by myself and did not know anyone else there, it was just me and the band. The Visions \textgreater \enspace  Phil's Farm was what sealed it for me. I hadn't felt that type of intensity from a band before. I wasn't around in the mid-90's to get all the incredible Phish shows. This was our generation's jam band. The second set was all a blur for me at this point, but that end of the first set was the reason I am still seeing them today.}
\Review{05-06-06}{The Avalon Ballroom, Boston, MA, USA}{cMags}{This was one of the weirder shows that I have been to. So the old Avalon (which is now the House of Blues) used to have a club night, like a lot of venues do. This show started at exactly 7PM, and at that time, there were probably 200 people still outside in line. It was one of only two shows, that I wasn't inside for the beginning of the show (the other being 9/8/11.) I was outside until the end of GYMRH, and I tried to get in with my fake ID. No luck and I got it swiped, so I wasn't in a good mood when I got in because that was my baby haha.  The Blue Echo will go down in history as one of the best jams the band has ever done, and I still stick by that to this day. It also had the debut of Words which I didn't realize hadn't been played to this point.  The Jajunk opener was fire and I got one of my many Rocker's of 06. Good Ol Boys and the piano piece were good rarities to cross off.   The show was over at 10 PM but it feature the 2 new songs that I had not heard, so it was nice to hear them.  Overall it was a weird show but they packed a punch in what was probably my shortest UM show ever.}
\Review{09-30-06}{Higher Ground, South Burlington, VT, USA}{cMags}{Coming off an incredible show from the night before, everyone in our hotel room slept in pretty late. We all walked around Burlington during the late morning/early afternoon, then made our way back to the hotel for the pre-game.  The show started off with an extended Plunger jam into MITA, which I had heard at the Hampton show 2 months earlier. 2x2 was standard, then during the Utopian jam, Brendan and Jake switched to their acoustic guitars. This was my first experience with acoustic UM and it was definitely a fitting time to do it as well. Nothing else worth notating, but the last 3 songs of the first set were really fun and different than the UM that I was used to.  Pay the Snucka 2nd set opener was nice, but No More Tears was definitely out of nowhere and I still listen to that version to this day. In the silent breakdown part, they sing a verse of Total Eclipse of the Heart in homage to Old School which was released about 3 years prior. The big jam of the set was The Triple Wide. During the jam, they busted into a lyrical stew and I remember Grover standing next to me screaming out something like "Skyline Stew, Skyline Stew!" I just laughed as he was like a kid in a candy store. I guess this was the jam that turned into Spires? IIRC. Anyways the rest of the set (Words, ITK) were standard. However, Rosanna was a really cool cover choice to finish it off, and after the finishing chorus they went into a jam. No other than Mrs Robinson's Strut. This is one of my favorite repeated stews and it was great to get it after my real first big run with Umph.   Overall it was a great weekend and I will never forget it.}
\Review{10-21-06}{The Avalon, Hollywood, CA, USA}{SourPatch}{My first time spent in LA just with friends, this venue was right on the edge of Hollywood... with like, strange vibes, really superficial people. And they came out starting with Syncopated Strangers, which was like a perfect complement... and the sound of this show fits really well, acoustics and what not.  At the end of Sync, when you're expecting that finishing major resolution, it comes straight in with a punch from an abstract intro to Hurt Bird Bath, that turns you inside out. Great 1st improv, and after the heavy hits, goes into this eerie slow composition, turning really heavy, it's giving me pins and needles writing about it. To me, it seemed like a perfect reaction to the environment.  Check it out, at least those two songs!}
\Review{11-02-06}{The Barrymore Theatre, Madison, WI, USA}{40sThemeWI}{Well....for starters the HBB sandwich in the first set is disgusting and there's umvideo on YouTube to prove it. Got my first Spinal Shaft (4th UM concert at the time) and let me say it's a doozy. The Jimmy Stewart turned into what is known as Red Tape I believe. But it's the Stew out of Groove Holmes that told me this was going to be a good 2 nights in Madison!!! A must hear for any fan! 5/5}
\Review{11-17-06}{The Tabernacle, Atlanta, GA, USA}{mikenpfafftown}{My second show and first two-setter is still a favorite of mine.  I just dug out the UMlive last week to give it a relisten. First set highlights are the Push the Pig, N2F\textgreater \enspace Thin Air with Sam Holt and the acoustic ITK.    It's the second set and encore though that put this show in the must hear category.  Opening with Jimi, then good ole Ringo set the room on fire.  I had one of those It experiences during Words.  Tears were spilled and I was left with nothing but love for this band who could craft such a beautiful song.  I was pretty much butter by the time they finished the N2F so it didn't really matter what they played thereafter.  Encore is really fun.  Zappa \textgreater \enspace  Kiss!!!  WTF indeed.}
\Review{11-17-06}{The Tabernacle, Atlanta, GA, USA}{OceanBillyWaves}{This was also my second show, after seeing them at Bonnaroo on 6/16. I loved them the first time because I had been listening to Anchor Drops on loop in my car for about a year before I got a chance to see them. But I would have to say that this was the first show where I 'got it,' in the sense that the music moved me in a way I'd never had a band do before. Might sound trite, but it's the truth.   I also have a fond place in my heart for this show, because it was the first show I ever saw at the Tabernacle. Wow. A bunch of Tabby memories later, I can honestly say that there is no place I would rather see an Umphrey's McGee concert than that venue. The energy was off the hook that night, as it always is in Atlanta, regardless of venue.   The musical moments that stood out to me were the Walletsworth\textgreater \enspace N2F. I could see those songs at every show from here on out and be happy as hell. In the Kitchen was great as well.   In the second set, it's hard for me to think about anything other than the Hendrix Jam on Power of Soul to kick it off. Talk about fire to start off a ridiculous second set, both in terms of the band being on top of their game and a kick ass set list. And the 2nd Self, Dirty Love \textgreater \enspace  God Gave Rock encore was amazing.}
\Review{06-01-07}{Electric Factory, Philadelphia, PA, USA}{alexankh}{My first umphreys show.  This is a first set that features almost no improv outside of the opening JO. This opening JO is a dark, bass driven theme that offers some nice keyboard support from Jake early on with dueling guitar riffs toward the end. I always hoped for this JO to pop up again, but it hasn't yet so far. Alex's house replaces both segments of improv usually associated with DBK. I think this works nicely, the outro of alex's house drops nicely into the end of DBK. I frequently revisit this opening 40 min segment.  The second set picks up some steam with N2F. During the lengthy jam (track length is about 23 mins for the first half), Allen from the biscuits replaces Kris on the drums (for his birthday jam!). The first half of the jam is kind of lackluster, not much going on, then Allen kicks up the tempo and the jam starts to take off. FF was a treat at my first show, it was and always has been a favorite of mine. The improv out of FF is downtempo and showcases some soaring guitar riffs from jake and a nice jam that leads back into the ending of N2F. Brendan breaks out the booty wax for the hangover reprise and gets the crowd involved with the set 2 closer.  Standard snucka encore. During jakes solo section, I remember he was playing with this massive novelty size pick. This thing was the size of a dinner plate. It was kinda cool to watch and hear him rip it up as bras and panties were thrown on stage. Snucka ends as the boys wish us safely on our way home and warn us in the distorted voice not to let strange people touch us in any weird way.  A fun show, nothing too mindblowing, but we all have to start somewhere}
\Review{11-15-07}{Amos' Southend, Charlotte, NC, USA}{okeefemail}{This was my first show. A non smoking rock show in 2007 was unheard of so I assumed they were squares, my how times have changed. Had no idea who I was seeing. Went to catch a buzz and try to get laid. There was about 400dudes and 9 women. PW into Nemo it was the beginning of a new addiction.  Got thrown out about set break for firing up a jib in the joint but ive got it on cd.  It was cold as hell that night for Charlotte.}
\Review{04-10-08}{Revolution Hall, Troy, NY, USA}{rondackmtns1}{This was my first Umphrey's show — and a real sizzler. The boys came on after my first few Pork Slaps at the bar and proceeded to melt face with a tight and intimate club show. World\textgreater \enspace Nemo\textgreater \enspace Prolwer is my pick with some great Chinese intervals. Billy Jean is an obvious fit to sandwich with Regulate. Miss Tinkles brought the house down before a rock-solid Floor encore.   Being it was my first show, and having only heard a few Umphrey's songs on Jam On and YouTube, I didn't quite get what was going on in front of me. We picked up the soundboard on the way out and cranked it the whole way home. It was then that “I got it," and I've been a Umphrey's fan ever since.   I’d keep this recording within arms reach.  A special show for me and an awesome venue where I've had some good memories. Too bad Rev Hall stopped hosting shows ...}
\Review{05-23-08}{"Summer Camp Music Festival" Three Sisters Park, Chillicothe, IL, USA}{bobbyluv}{When it comes to UM at Summercamp, I think this is THE show that Umphreaks would agree is the top dog.  Up to 2008, UM had slowly been usurping their dominance over Summercamp leading up to this show.  2006 saw the 1st time that UM got a headlining set/show on the 'main stage' and that began the ascension up the SC throne.  2007 also gave UM a headlining show, but 2008 set the stage for SC to be UM's festie to dominate, if ya ask me. 1st set began with ideal weather.  Cool and sunny.    Strong Floor out of the gates that segued nicely into Mitten rife with Jetson's teases.  Nothing super noteworthy here, but solid nonetheless.  The real fireworks came with what quite possibly may be the best Utopian ever.  Super lengthy jam that gets super dancey with Kris nailing on the e-drums.   There are 3 distinct sections to the improv, each one topping the other culminating to an amazing peak.  Killer soundbites from Big Lebowski and GoodFellas sprinkled throughout.  Top Shelf UM at its finest!!!  In between sets the temperature dropped a good 10 degrees, and the start of the set saw the boys in hoodies and long sleeves.    Strong intro\textgreater \enspace Mulche's was fast and furious but the real fireworks began with the Divisions\textgreater \enspace Phil's\textgreater \enspace Divisions.  GREAT segue into Phil's (super slinky) and this Phil's is not to be missed.  They deviate so far from the theme that it goes unfinished\textgreater \enspace \textgreater \enspace \textgreater \enspace Divisions.    DBK\textgreater \enspace Wappy\textgreater \enspace DBK is a super strong combo as well.  Once the DBK finishes, there was no doubt that UM had played their best set to date at Summercamp.    Shine On encore just seemed to fit perfectly.   After this show is where we met Nickmo!  Great night indeed!!}
\Review{07-31-08}{Lincoln Theatre, Raleigh, NC, USA}{mikenpfafftown}{After a rather pedestrian set at Koka Booth Amphitheathre opening for STS9 earlier in the day, I kind of expected to get our asses handed to us at the late night Lincoln show.  After waiting and waiting and waiting, the show finally began I believe a little after midnight.  This set was a complete about face from the daytime set.  The band seemed about as amped as I'd ever seen them.  Could've been the tiny stage they were playing on or the rowdiness of the crowd, but I don't think I've ever seen them this loose before.  Check out the skullfuckery in the first Voices Inside My Head/Snake Juice jam.  I also think this is the best encore I've ever seen by any band. Great night of Umphrey's McGee.}
\Review{08-09-08}{Up North Festival, Hiram, ME, USA}{DREDLOX}{Not really posting a review but I wish the Up North Festival stayed alive longer than the ONE YEAR it did.  This show featured 4 of the BIG GUN songs in UM's repertoire including Utopian, HBB, DBK, and N2F with Floyd in the encore slot.   They were headlining this night so played a 2 hour set.  The encore was roughly 30 minutes long.  A little known fact amongst Umphreaks is that THIS SHOW WAS JEFFERSON WAFUL'S FIRST TIME RUNNING THE LIGHT RIG IN A LIVE SETTING FOR UMPHREY'S!!!}
\Review{09-13-08}{"Harvest Music Festival" Mulberry Mountain, Ozark, AR, USA}{FrontPorchesR4Sittin}{Hurricane Ike epicness. Main stage rained out, practice gear set up in the coverd Harvest Tent. Rain like I've never seen before; mud above my ankles, tent and many other things destroyed/blown away. Next morning, all roads leaving the Mountain were closed (downed trees). Most insane show I have seen to date.}
\Review{10-17-08}{Smith Opera House, Geneva, NY, USA}{kmdeadhead}{One of my favorite shows:  one of the best Robot Worlds I have ever heard and a very large Pony led Phil's that goes from Dance \textgreater \enspace  One slow verse of Peeps \textgreater \enspace  Dance \textgreater \enspace  RAWK  Also some great improv in Tribute, Water, Bottom 1/2, and a haunting lyrical stew in Sweetness}
\Review{02-14-09}{The Barrymore Theatre, Madison, WI, USA}{umphalex}{This was my first Valentine's Day show and it was one that never dissapoints.  First and second sets both deliver big time.  The August opener is huge and goes into really good dance grooves.  Syncopated Strangers is 18 mins long and the jimmy stewart inside of it had the whole place dancing!!!  Sociable Jimmy is huge too, with the Xxplosive jam just started this show out with pure energy.....  Probably my favorite All in time I've still ever heard (its now 2013) and the mullet over is always a treat.  Great four night run! Thanks UM, Madison loves you!}
\Review{04-05-09}{Toad's Place, New Haven, CT, USA}{mja271}{This was a really great show.  Getting to see a full on acoustic show is something that was a big treat for me.  As much as the band shreds electrically, I've always been impressed with the beauty and subtlety of their acoustic style.  This can be seen here in the great first set run of Water \textgreater \enspace  Sweetness \textgreater \enspace  Fearless.  The cover selections were on point; Floyd, Blind Faith, Wings, Seger...can't beat that.  Really enjoyed the Nemo jam, hearing a rare Never Cease, an energetic Peeps, and the debut of Ride On Pony.  Great vibe and energy from the band (they were especially tipsy for much of the show for Kris' birthday) and excellent playing.  A great view of a different side of UM.}
\Review{10-10-09}{Youth Building at Exposition Gardens, Peoria, IL, USA}{OrneTTe}{This show was originally scheduled to be on the Peoria Riverfront but it was super cold all that week so the show was moved indoors. I was a little bummed about the move but was happy about a hometown UM show.  The venue at Expo Gardens looked like an old high school gym or cafeteria; the bathrooms like high school locker rooms. The first set was solid but nothing really outstanding.  The Fuzz had the slower funky feel and I believe was a nod to the Peoria Police Dept. who lined the walls, Blues Brothers style.  The set closed with the short-lived Cold Smoke, which is just Go To Hell with lyrics. I was on a Beatles kick during the time so I Want You was a nice addition.  The second set was a little more interesting.  If you have not done so, LISTEN TO THIS MUCH OBLIGED! It may be the best MO of all time. N2F\textgreater \enspace Bottom Half was pretty good.  Red Tape was nothing special, like most Red Tapes during this time.  A Rush cover is always ok in my book. Encore was a lot of fun. Who doesn't like Wife Soup?  And the transition back into N2F is pretty darn good.  Overall it was a pretty solid show but a total shit show when it came to the crowd and venue.  I saw girls dropping like flies from being too drunk and the men's bathroom became a swamp of urine and overflowed toilet water.  With the cops there, it just made it feel like an old school rock show.  Fun times.}
\Review{11-13-09}{Higher Ground, South Burlington, VT, USA}{N2FBoston}{I've been to 45 UM shows, and these three higher ground shows are hands down my favorites, with this night being the highlight. It was Pony's birthday and everyone in the crowd and the band were going ape shit.  Highlights: -The mulches jam is an epic dance party -Stasiks's bass line during sociable jimmy jam! -Mike's Kitchen... one of the best jams I've ever heard. The communication is amazing, and they really take you on a musical adventure with multiple different sections, each segued perfectly.}
\Review{11-15-09}{Port City Music Hall, Portland, ME, USA}{railroadearther}{check out the The Crooked One[1] \textgreater \enspace  Utopian Fir \textgreater \enspace  Big Heart \textgreater \enspace  Utopian Fir segment for some top-notch UM.    Phil's Farm and FF \textgreater \enspace  Tomorrow Never Knows are worth listening to as well.  Intimate Sunday night throwdown in Portland, Maine!}
\Review{12-31-09}{Aragon Ballroom, Chicago, IL, USA}{umphalex}{For some reason this NYE show always stick out in my mind as one of the most memorable nights of mine...This was my second NYE show and it delivered on all fronts.  The first set is a real treat with Cemetery Walk 1 getting ppl in the mood early for a rager, which was followed by a short but great triple wide.  This was my first headphones and snowcones which is always welcomed and should be played more!  The whole second set is gold, and the tower of power cover takes the cake!  Kris Myers is truly amazing, vocals and drums.  Set 3 contains alot of good jamming, starting with the much obliged that gets super funky to bring in the new year.  Phils farm still may be my favorite version, good bass wapping fun...  Of course turn and dub is always welcomed, but I'll never forget stasik in his shiny pink shirt singing cant take my eyes off of you! Hilarious!!!    Reelin in the years was jsut ppl having fun and enjoying being at somehting as special as an UM NYE!}
\Review{02-06-10}{The Tabernacle, Atlanta, GA, USA}{dubzz}{This for me also marked my deflowering at the hand's of UM.  The Jaws theme was played as the band took the stage and set up.  Added an erie effect coupled by Waful's reds on stage.  The jump into JaJunk was set up perfectly with this.  MO \textgreater \enspace  1348 was a major highlight for me.  The Wife Soup transition back to JaJunk was seamless and definitely deserves some attention.  A lot of heavy hitters (Bridgeless, Wappy, Cem2) and the crowd made it a really high octane show.  Morning Song was probably the slowest moment of the show and was still masterfully performed.  Little did I know until a handful of shows later and the DVD release, how special of an experience it truly was. Remains one of my favorite shows to date! 9/10}
\Review{02-26-10}{House of Blues, Boston, MA, USA}{mja271}{Solid show.  This was probably the first time I saw UM and left without really feeling the high that they normally give me, but it was not without its moments.  The first set started off great with nice jams in Bottom Half and Higgins, but never really picked back up.  Always nice to see Uncle Wally pop up, but the In The Kitchen and Push the Pig sit ins were very disappointing and never really took off.  The second set was definitely a different story.  I love Mantis, so that was a great start and Ocean Billy was strong with a nice -\textgreater \enspace  into 2nd Self.  The DBK/Zep segment was great with the exception of a bit of an awkward segue into the cover.  The Triple Wide was above average and a nice set ender.  The encore was also a bit standard, but a solid way to leave a show.  Overall, the show was just a bit lacking.  The band never really fully hit their stride I feel, but still a good time.}
\Review{02-27-10}{Electric Factory, Philadelphia, PA, USA}{3x40oz}{This show was sort of strange for my tastes in UM...lots of ups and downs in the first set. The Olympic walkout and opening Wappy portended a strong Saturday night show, but following it up with standard versions of Peeps and CWI seemed to bring the energy in the room way down. Snucka was initially welcomed, but I found the sit-in jam to be a bit noodly for my tastes. \#5 and Sociable are two of my favourite compositions, and closing with two brand new tunes and Snucka III was an excellent move. Booth Love definitely got the room moving, and I remember wondering if the Linear was an obscure Police cover (first time played with lyrics, so I was totally in the dark.)  Set II started very strong, just like the first set, but managed to keep it's momentum rolling throughout. An unfinished Divisions with a nice funky MJ jam juxtaposed nicely with the powerful darkness of The Floor. I would have liked some improv in the Ringo, but this was the first Glory I had caught since my first show four years earlier at the E-Factory, and I thoroughly enjoyed it. The Abbey Road medley was another great rarity to catch, featuring vox from BB, Jake, and Joel on the various songs. 2x2 is a fantastic f*cking song; I was ecstatic to see this one drop late in the second set. A quick Mantis Ghetts into a full-on Baylor singalong Divisions ending was a great ending to the set. MP is perhaps my favourite Jake song (right up there with Bad Poker and Synco); a quirky tune with a strong dose of Zappa-ish humour and musicality. I expected Package's dueling guitar coda to end the show, so a focused CWII was a bonus that sent me out the door dancing.}
\Review{03-11-10}{The Orpheum Theatre, Madison, WI, USA}{umphalex}{One of the greatest first sets I've ever heard!  The floor is pretty traditional but then 2X2 has this sick asian sounding jam in it...  Turn and Dub is like 18 minutes of good phsychedelic jam followed by a great american with 2 big dance jams in it...Sweet sunglasses is a great cover and a good set closer.  Still one of my favorite Tribute's to start out set 2 which had a Law and order intro with stasik slappin the bass.  Highlights in set 2 for me was Raymond and Fool in the rain.  Madison is a great setting for UM.}
\Review{06-30-10}{"Summerfest" Henry Maier Festival Park, Milwaukee, WI, USA}{umphalex}{This show is seriously under rated and never talked about.  But when it's a general admission \$10 summerfest ticket and UM plays like this, WOW!  Opener of resolution with two seperate jams wrapped around the tune, first jam is a rocker, and second jam is funky...  Pretty standard versions of PW, S4, and then an always wonderful zeppelin cover to get the party goin.  Nothin too fancy can be heard on UM-Hall of Fame and is one of the greatest ambient UM grooves I've heard to date..its tasty.  Push the pig has a good healthy jam, and Milwaukee was diggin the harder groove that "in bloom" brought...  One of the coolest Fuzz jams I've ever heard, its like bar room rockin jamboree shit..really is quite killer...  Encore embodied some hendrix teases and ended the night in serious fashion!  UM always rocks out at summerfest}
\Review{07-09-10}{"All Good Music Festival" Marvin's Mountaintop, Masontown, WV, USA}{TalonMcgee}{There were technical difficulties for the first 20 seconds or so of booth love until the full sound system kicked in.    Highlights were the miles Davis cover and the divisions\textgreater \enspace  I'm on fire \textgreater \enspace  divisions  Pretty sure this was the second time I'm on fire was played and I was lucky enough to catch the first one in Cleveland.  No one seems to mention the ZZ Top jam in Made To Measure, Waitin on the Bus! It fits so perfectly and I wish they'd do it again sometime}
\Review{07-09-10}{"All Good Music Festival" Marvin's Mountaintop, Masontown, WV, USA}{elBerto}{Great day setter. My brother and I caught Jake and Pony standing next to us grooving to Femi Kuti earlier in the day. I told 'em to "play that funky Booth Lovin'" knowing it was one they had been polishing. The Miles Davis cover took me by surprise, very cool to hear. Divisions\textgreater \enspace  I'm on Fire\textgreater \enspace  Divisions was so nice.  The sweet little old lady mayor of Masontown introduced the band as a light rain broke the Mountaintop heat. I believe she flubbed on the name.}
\Review{07-17-10}{The Lawn at White River State Park, Indianapolis, IN, USA}{YourPalJay}{There's a lot of love for Set 1. I like Words. Bird Bath was strong. Girlfriend was a monster closer. But Set 2 had a crazy intensity to it, especially the first half.  There were thunderstorms all around the venue and everyone would agree it wasn't a matter of *if* the show would be cut short for weather, it was *when*. So the band took a minimal (10 min?) setbreak and came out with the intention of playing as long as they could. What resulted was a Set 2 where each of the first 4 songs was played as if it was the show closer. Great peaks, huge solos, major intensity. All with Waful's lights playing hand-in-hand with the lightning backdrop.}
\Review{07-17-10}{The Lawn at White River State Park, Indianapolis, IN, USA}{Hugger}{$\wedge$Yep!  Gotta agree with the above reviewer about the Talking Heads cover.  In fact, that whole first set was so spot on, I was caught off guard when they walked off for set break. Seemed like they had just started.  Great show from front to back.    Watched the first set from the rail, but got caught by the short set break, and watched the 2nd set from the top of the hill.}
\Review{08-07-10}{Stone Pony Summerstage, Asbury Park, NJ, USA}{elBerto}{This was a very unique show in my opinion. Highlights galore... ITK\textgreater \enspace  tribute to Stone Pony legends Bruce and Joel\textgreater \enspace  ITK, Kula (with Kula tease?), Blue\textgreater \enspace  Keefer\textgreater \enspace  Echo... great night on the boardwalk!}
\Review{10-21-10}{Mr. Small's Theatre, Millvale, PA, USA}{TalonMcgee}{I was still not familiar with the whole catalog at this time and thought \#5 was just a SICK jam in AIT, turned into one of my favorite songs after that.  13 days is always a treat and everyone was boogieing down to reelin in the years  As was stated, the ringo jam is prob the highlight of the show  I felt the AIT reprise should have closed the second set and it was a weird flow to end with thin air after a rocker}
\Review{10-21-10}{Mr. Small's Theatre, Millvale, PA, USA}{driver}{Much of this show is a little bit hazy for me, but it was probably the trippiest UM show I've ever seen.  Check out the Push the Pig (the guitar sound drips out of the amps in a most psychedelic way.    Reelin' in the Years was a crowd favorite, and the Ringo jam is worth a listen, as well.    All in all a very fun show in a very awesome little venue.}
\Review{12-31-10}{The Riviera Theatre, Chicago, IL, USA}{umphalex}{I would have to completely disagree with the final comment on the first review of this show about the other covers slowing down the show.  I can say that this was my 5th NYE show with UM and my 35th show of UM all together and thought ALL of the cover choices were spot on.  The Demolition Man cover was excellent, UM has covered a ton of Police over the years and this one was a real treat off of "ghost in the machine" album.    And then the Beck cover of Mixed Bizness to bring in the new year was some great funk with fun lyrics!    Definitely highlights of this show are the whole first set being a free flowing complete piece of music that was quite beatiful.  Also Kris Myers putting on his soul shoes and doing James Brown right in set 2 was a real treat!  The All in time of this show will be forever in my mind of how far UM can take it, in all different facets and forms of music.  And dont forget about how badass it gets wheen cody dickinson does washboard on the slacker.  Jake and Cody get dark and heavy and wonderful.  Great show!}
\Review{12-31-10}{The Riviera Theatre, Chicago, IL, USA}{Scopeless}{My second show after a huge gap from not going since '06.  I got deeper into UM after my friend gave me a huge stash of free '09 UM tracks.  I then bought Mantis, I then bought Anchor Drops, I then was hooked for life and went to my second show...THIS show.  The most memorable part of this show involves a story. -------------------- Since me and my wife were UM newbs.  We didn't understand there was a VIP section.  We got to the show early and sat in the balcony.  As the rows filled-up, a security person stood in the aisle next to where you come into our row.  The show starts and a waitress comes and asks if we want a drink.  I'm thinking, "Wow, this is some service at a concert."  We order drinks and get them.  Midway through the first set, a guy in a Homer Simpson shirt comes to sit next to us.  He asks if he can, and we say yes.  He says cool and smokes us up.  He then gives me something else...a nugget of something green.  I say, "Oh, sorry man.  I have anything on me to smoke that with."  He says, "No that's for your ride home for letting me sit here."  We are stunned and he leaves the seat after the song is over.    At the beginning of set two, someone in front of us gets kicked out.  I notice it's because they don't have a ticket or something.  I ask the people near us what happened and they say that the people didn't have VIP passes.  I turn white and realize that me and my wife ALSO don't have these passes.  We did it on accident since we got there before security showed-up.  We laid-low for the rest of the show and had a blast.  But now it all made sense, the waitress, meeting Joel's parents, people with bottles of champagne, the guy giving us a free nug to just stand there.  WE WERE ACCIDENTALLY IN THE VIP SECTION THE WHOLE SHOW! ---------------------  3.5-4 of five.  The opener was great.  I love when the opening of a show kills.  It really sets-up the show to be a great one throughout.  The debut of Deeper -\textgreater \enspace  N2F started that track off in a memorable way.  The Bright Lights sax jam was very underrated.  The National Anthem debut was out of the park.  As well as the James Brown tracks.  Nice job, Kris!  The other cover choices really slowed the pace of the show.  If you take them away, you're left with a great UM show.  Which just shows that sometimes UM doesn't need their covers to make a complete show.}
\Review{02-17-11}{The Orange Peel, Asheville, NC, USA}{UtopianSludge}{Ever since me and a few of my buddies made the trip from Auburn, AL up to Asheville, NC for this one it has been known amongst us as "The Show".  It was a fantastic atmosphere as well as a kick ass setlist.    The first set was killer with a dance party in red tape. sweet home alabama teases in bad poker. and epic tinkle.  the burning down the house cover was awesome. the moog theremin plus jake makes for a trippy and mesmerizing jam.    The plunger after the set break was classic with an intricate and deep jam that jake and BB rocked.  Last man swerving had a badass progressive jam.ROUNDABOUT!!!!! enough said.  all of that goes back into plunger all perfectly executed.    Then the encore was completely opposite sides of the spectrum. A great show! i recommend it to a new found UM fan or a seasoned vet.}
\Review{03-02-11}{The Barrymore Theatre, Madison, WI, USA}{umphalex}{Let me start out by saying that this is a pretty underated show.  It's definitely pretty proggy and out there at times but a great show.  The Miss Tinkle's Overture is still by far the best version I've ever heard to date and I've been to 50 plus UM shows and have downloaded tons tons more.  It is pure energy and pumps you up with a sort of metal dance party.  The visions with the blues for los angeles jam is down right nasty....deep trancy, jazzy, jam that is super tasty and not a usual sound for the band.  Set 2 Highlights were of course the nice beatles cover, but the Crooked one into Utopian is big and bad.  The crooked one gets a little dark but very jammy and the Utopian fir gets dark as well but has a really nice tail end of reggae that's a bit longer and extended than normal.  Hot for teacher was real appropriate since the teachers were all striking up at the capitol and made for a great end.   Night 2 of this run was the bee's knee's though....}
\Review{03-03-11}{The Barrymore Theatre, Madison, WI, USA}{Scopeless}{My second favorite show of the year behind 11.5.11.  The first set was perfectly executed.  The opener into a Jimmy Stewart with Lyrics Intentions Clear was the right way to open a show.  It was like a book with an engaging chapter one.    The Haunt and Divisions jams don't get talked-up as much as Intentions Clear (which, by the way, is now the UM tune, Teresa), but they should be lauded as highly.  The Haunt peaks well and has a great structure that can be used in a future song.  The Divisions is MONSTROUS.  Over 24 minutes of epic UM performance.    The DBK was great, but then the set starts to drift a little bit, imo.  I'm just not a fan of Mullet, standard Deeper (newer versions have been terrific though), and It's So Easy.  It was almost as if Dutchman -\textgreater \enspace  DBK was SOOOOOO rocking that UM lost their mojo right at the end.  It's what I feel holds this show back from being in discussion as the best of the year, but it comes ever so close.}
\Review{03-11-11}{Crystal Ballroom, Portland, OR, USA}{jnumber1}{This could very easily be my favorite second set ever. Maybe because I'm a local, or maybe it was 80's night happening downstairs and spilling up to the show, I don't know. Was it just me or was that a Things Can Only Get Better (Howard Jones) tease by Myers at the end of the first Snucka? Can't wait to do it all again in a couple months.}
\Review{07-01-11}{Simon Estes Riverfront Amphitheater, Des Moines, IA, USA}{N8ing\char`_2\char`_Phancy}{With the Heat and the fireworks this show was one for the books. Great versions of Rocker pt duex and Water (seems legit playing right next to a river.) Then somewhere around the merge into Syncopated Strangers from Tribute things got explosive. Fireworks from the Cubs farm club stadium went off...it was quite the treat but not the only one...As Walking on the moon started getting deep...the Des Moines pops go the fourth fireworks went off...if you DL the show you can hear the fireworks going off and how the band especially Jake played into them making for one memorable first set. 2nd Set was fire from the start into a miami vice vibe twords the end. Best All in Time sandwich ever! Africa also seemed fitting once again due to the heat. Which was brought by mother nature and our friends our pals....Umphrey's McGee.}
\Review{07-15-11}{"All Good Music Festival" Marvin's Mountaintop, Masontown, WV, USA}{TalonMcgee}{Shortened set due to Furthur playing passed their allotted time, apparently Phil got lost during set break. x\char`_x  Despite that, the boys skipped all filler and pumped out the jams  This is still my favorite Puppet and I was super surprised at how well they did Tom Sawyer   Encore kinda disappointed me with a cover and the horns in jajunk were quite lackluster but nevertheless it was a great show}
\Review{09-03-11}{9:30 Club, Washington, DC, USA}{3x40oz}{Really enjoyed this show live...classic 2011 UM shit. The opening AIT had a nice jam. Never can catch the Red Tape teases but the Life During Wartime tease was very apparent live and on tape. Butter smooth segue into PS. The Water \textgreater \enspace  Day Nurse \textgreater \enspace  August section felt a little disjointed with the juxtaposition of Water's tight composition, the electro-dance of Nurse, followed by a soaring August. The August jam would eventually become the opening riff of Similar Skin. Deeper jam was decent but not particularly noteworthy.  The AIT drop out of Prowler kind of caught me off guard. I thought for sure that would be saved until the end of the second set. 1348 seemed like it was about to take off when they segued to 2x2. I wish they had milked that jam a bit more. 2x2 is always a pleasure to catch. The band really liked the Tink's/Masoka Tanga pairing in 2011. I recall it happening a couple times. If they really did play Billie Jean off the cuff for the encore, that's fucking sweet. The crowd ate it up and it provided a nice transition into the second half of 1348.  TL; DR - All In Time, August, and 1348 are the highlights. Solid show all around.}
\Review{11-02-11}{Northern Lights, Clifton Park, NY, USA}{Pookells}{First off, I have to say that I think this is the best show from 2011, and those who attended this show were truly blessed to have seen this.  Set 1 kicks off with Example 1.  The Example 1 is pretty standard until they get to the jam section of the song.  The jam in this is a mid tempo rocking jam with tons of solos going all over the place, and it is this jam that pretty much sets the mood for the remainder of the show.  They get into a high-energy version of Got Your Milk that, again, has a hard rocking stew with plenty of guitar fireworks from Jake and Brendan.  It's probably the best Milk I've heard these guys do.  Milk segues quite nicely into \#5.  \#5 rocks pretty hard as well and has a sweet heavy stew in it as well.  Milk -\textgreater \enspace  \#5 clocks in at over 25 minutes in length.  They do a nice cover of Fool In The Rain, and although Brendan is no Robert Plant vocally, his vocals are adequate in this version.  While this version isn't bad at all, it is probably the weakest link in this show (I use the term "weakest" in the loosest sense of the word).  Search 4 comes out just as hard rocking as the Death By Stereo studio version and fits in perfectly with the rest of the hard rock in this set.  The set finishes off with Last Man Swerving \textgreater \enspace  Believe The Lie.  Last Man Swerving is an 18+ minute treat, and has a nice long jam that can only be best described as 70's prog-disco.  Not funky and not hard rock either.  Imagine Animals-era Pink Floyd with some disco elements and you get the picture.  Believe The Lie rocks harder than what you normally hear in this song live and has some nice 70's prog that seems to be somewhat inspired by Kansas, but is done in UM's unique way.  Check out the guitar solos that kick in at the 7:12 point of the song - Jake and Brendan do some serious (but short) shredding!  Set 2 kicks off with a nearly 31 minute long DBK.  Again, keeping in the hard rock/prog theme of the show, this is one of the hardest rocking DBKs they've done. If you don't catch yourself playing air guitar during the first 8 minutes of DBK, then you need to check your pulse. At around the 8:05 mark, the band throws down some of the same style of 70's prog-disco that was done on Last Man Swerving without repeating what was done during Last Man Swerving (I hope that sentence made sense). Between 8:05 and the 21 minute mark, there's a lot going on with this jam as this jam conjures up Animals-era Pink Floyd, jazzy interludes and even some Metallica-like shredding at around the 20:30 mark.  The jam changes into a jazzy section at the 21 minute mark that lasts until the 26:40 mark.  At 26:40, the jam gets heavy with seriously fast rhythm guitar that puts Metallica to shame and then goes back to the jazzy section.  The last minute is the outro riff of DBK.  Next comes a hard rocking I Am The Walrus that is quite stellar with some kick-ass Jake solos throughout.  Even The Bottom Half rocks harder than usual and UM takes the song into a slightly different direction than usual with the Simple Gifts jam, and contains a hard rock ending.  Slacker, like every other song here, is a harder version with a bluesy section at about 2:40 that sounds like ZZ Top experimenting with jazz styles.  And then if you hadn't had enough, they bring down the house with an insane Wizard Burial Ground that will just leave your jaw on the ground.  Even Bright Lights as the encore is a hard rocking version as well.  Overall, this show is completely worth the purchase!  As I stated in the beginning, this is the best show of 2011.  Unfortunately, it's also overlooked as this show was sandwiched in between the 10/29 Hauntlanta and 11/5 Milwaukee shows.  This is a 13 song show, which is very reminiscient of the 2006-2008 era, plus the 5 song 2nd set is a throwback to that era as well.  It displays the harder side of UM and is a consistent theme throughout the show.  You can check out this show on youtube.  Just type in umphrey's mcgee clifton park and watch the videos of this show that were put up by axanodus.   Enjoy this show!  Well worth the \$\$.}
\Review{11-25-11}{Aragon Ballroom, Chicago, IL, USA}{umphalex}{These two Thanksgiving shows will always have a special place in my heart!  Epic sets both nights and UM truly was destroying all there jams on these nights.  Red tape is unusually "steely dan" jam esque and I really dig where it ends up.  Wappy sprayberry is hands down the best version I've ever heard in 45 plus live shows and listening to hundreds...}
\Review{01-21-12}{Best Buy Theater, New York, NY, USA}{owenbroch}{Both of these shows were great, but the second set of night 2 was rawking. The newer Miami Virtue into an ever-emotional Glory was a great start, and then it was hammer to the floor  right up til the end of the set. Bridgeless is a personal fav and Hollywood Nights was a nice treat that had everyone jumping and singing along. They came out for encore and Jen performed an amazing rendition of At Last. Which was so good, my friend (whom also was at this show)just used this version of the song as his first dance at his wedding. Anyways, I digress... JaJunk, classic Umph's, i need say no more! UM Rawks!!  mm/}
\Review{02-04-12}{Super Bowl Village, Indianapolis, IN, USA}{BBQsauceNchickenwings}{I was pumped when I saw Umphrey's was playing a free show at the Super Bowl Village.  My buddy and I left from Columbus and picked up one more friend in Dayton.  When we got near the stadium in Indianapolis, the whole area of wild but somehow we managed to find a miracle open parking spot a block from the action. The village is basically a giant party formed by many independent parties:bars, stages, private tents, etc.  I had this fantasy that Umphrey's was going to fall under people's radar at an event like this and I would get up close....I was pleasantly surprised to find a massive crowd backed up the street to see UM.  The kids we ended up next to were from Indiana, but they had  been in Columbus seeing the Werks at the same new years show as us just a month before. Kris kicked it off wit the drum into Conduit, and they smoked this one as usual.  In the Kitchen went into a great dance groove before giving birth to Glory, truly a glorious choice this night or any night. i remember looking around and seeing peoples faces with a look like "WHAT?! Is it legal to rock this hard?! and in public?" when jake was doing his thing.  Out of push the pig also a miss tinkles that reached serious intensity during the peak...Baba O-Riley was well-recieved by the crowd.  For one set, Umphrey's still satisfied me until the 17th and surely made a slew of new fans.}
\Review{02-10-12}{House of Blues, Boston, MA, USA}{fussydutchman}{First off, if you're seeing Umph at HOB Boston in the future, get there plenty early.  A February line next to Fenway isn't all that pleasant.  We managed to get in during JaJunk, after waiting at least 30-40 minutes in line, and there was still a looooong line behind us.  I loved the Stew.  I loved the Walking on the Moon, for the flashback to my younger days.  I loved Puppet String.  I really loved the Divisions (as the political nonsense was just starting to get fun, Waful did an excellent red v. blue lighting concept during the soulful last part of the song; "All my...divided" had the stage split with blue and red, up to the "until it fades," where the lights went all white--thanks, Waful!).  I loved the Domino.  I always love me some Wappy, and to keep the dance vibe alive through Booth Love, followed by the always beautiful Haj.  Delicious show.}
\Review{02-17-12}{Lifestyle Communities Pavilion, Columbus, OH, USA}{driver}{This might have been some of the best UM I've seen to date.  The place was packed.  While I'm not a huge fan of this venue overall, the energy was good.    Eat and Got Your Milk made for a nice beginning to the show, and the Turn \& Dub was excellent.    Second set was really what made this show, though.  August was nice and the JJ\textgreater \enspace WW\textgreater \enspace JJ was top notch.  The WW jam is a must listen.    This encore was perhaps the best UM encore I've seen.  Nemo was a treat that I hope I see again soon, and the King Crimson sandwich was nice.  Red was SUPER dark, and Waful absolutely crushed it with the lights.  If you can find video, do it.  I wish that the band had finished with the vocal harmony left hanging, though, rather than coming back in for the final chord.  All in all a very solid show.}
\Review{03-22-12}{Showbox at the Market, Seattle, WA, USA}{Pookells}{This was first (and only, so far) UM show.  While this isn't the best show of 2012, it is a pretty damned solid show!  The show kicks off with Cummins that segues nicely into Crooked (which possesses a nice, but standard jam).  Intentions is great and has a great jam (vocals are a bit weak compared to other live versions).  Glory is pretty standard.  RtB is probably the best live RtB I've heard out of the other live versions I've heard.  Deeper sandwiched by Nemo is pretty sweet.  Now to the jam of the night - Smell The Mitten!  Clocking in at 15 minutes, Mitten has some sweet improv that includes a snippet of Steve Miller Band's "Abracadabra", and the last 5 minutes is just a dance party!  Set 2 kicks off with Tinkles, which was a nice set opener.  Virtue is the 2nd best jam of the night with a nice stew thrown in there.  Walletsworth is standard, but very good.  Let's Dance is quite faithful to the Bowie original.  Day Nurse is just a nice dance party, Conduit was OK.  The drum duel between Kris and Andy is way cool, haven't seen that on a lot of setlists.  1348 and The Floor end the 2nd set with a strong finish.  The Prowler \textgreater \enspace  1348 encore is OK, but way too short (probably due to the 12:30am curfew UM had to deal with).  All in all, pretty solid show.  Not 2012's best, but definitely not 2012's worst either.  It is better than the 3/23 show in Portland, IMO.}
\Review{04-27-12}{"UMBowl III" Park West, Chicago, IL, USA}{umphalex}{UMbowl 3 may be the greatest umphreys performance to date...its simply amazing how they completely get better and better year after year...I can recall after umbowl 2 thinking you couldnt play a concert that compares with it, but sure enough umbowl 3 crushed it.  It was nice to see my people vote in a little GD and we all enjoyed that a ton.  Too many high points to recap but set 2 and 4 are statements in how much better this band is than anyone!}
\Review{08-07-12}{"sUMmer school" Full Moon Resort, Big Indian, NY, USA}{N2FBoston}{This may have been "The show" from sUMmer school. Each night was special in its own way, but this show was especially memorable. The Phils Farm and DBK sandwiches were definitely the highlights, but pretty much all the jams were extremely tight and the more elaborate rehearsed parts in songs like Go to Hell and Mantis were played perfectly.  A little background on the debut of Weird Fishes...  At summer school we had the amazing opportunity to have one on one sessions with members of the band. My good friend Kyle Michaud had a lesson with Jake the afternoon of this show. During the session Jake started messing around with some chords and Kyle noticed he was dancing around the chords of Weird Fishes, but was missing a few. Kyle pointed this out, played the song with the missing chords... and that night Jake busted it out during the show. This is a great way to exemplify the amazing experience that was sUMmer school. By the end of the weekend it was hard to look at UM on stage as the epic Godlike musicians that I normally see them as, because we all felt more like a bunch of friends hanging out and appreciating good music.  Also... it was that much more epic when I saw them play weird fishes at red rocks...}
\Review{08-09-12}{"sUMmer school" Full Moon Resort, Big Indian, NY, USA}{N2FBoston}{It goes without saying that this show is a must listen - Stanley Jordan cannot be human... just can't be.   I over heard one of the guys from the band say after the show that Stanley chose Liquid himself. They played a great version of the song with a great solo by Stanley then as the song ended UM stepped aside and let Stanley do his thing on his own. It was amazing, to watch the band members look at Stanley the way we look at them, in complete and utter AW... Making Flippy Floppy is epic, the jam is straight fire. I don't know if I've ever seen the guys having that much fun on stage.  Another note on Stanley Jordan - He is the most spiritual musician I've ever had the honor to meet. Most of the people at sUMmer school got to talk to him and all the conversations were truly inspiring. After the show we all broke out into open jams and Stanley showed up and jammed with us for many hours into the night. sUMmer school was by far the most amazing, beneficial, and inspirational musical event I've ever attended.}
\Review{09-15-12}{Boulder Theater, Boulder, CO, USA}{skysoxfan}{What an incredible show this was! To follow up Red Rocks with this night was beyond amazing. It was a life changing show for me. I liked Umphrey's before this show, but now I can't get enough of them. I couldn't stop moving or feeling the music. From Joel's incredibly succinct keyboard work, Brendan's focus and yet relaxed performance, Jake's insane picking, Chris's and Andy's rhythm setting the pace, and Ryan's vibing on the bass --- I was definitely beyond in love, wet, and creamed when I left this show... I got Umph Love!}
\Review{10-26-12}{Riverside Theater, Milwaukee, WI, USA}{RobotWorldOrGTFO}{Finally got an Intentions Clear, Morning Song, a Padgett's, the list goes on and on.  This was the pop up set of all pop up sets.  White Pickle and Den are fourth quarter UM Bowl jams so its neat to see those out on tour after witnessing them once before.  Throw a second Mail Package and a Slacker on top of that as well?  Shit.  Bridgeless\textgreater \enspace Cherub Rock was insane, and Kris tearing it up with Mother?  Dopest of dope.  At first we thought this night was going to be the warm up for Saturday but holy god were we wrong.  Excellent Halloween run.}
\Review{10-26-12}{Riverside Theater, Milwaukee, WI, USA}{umphalex}{This night rivals night 2 at the Riverside in my opinion....both were phenomenal but this night is silly good.  Intentions clear gets really funky and jammy and then I went absolutely bolistic when I got white pickle into den...anyone who went to UMbowl 3 should have a deep appreciation for how insanely great these two tunes really are!  I called the Padgett's profile before the show and was going nuts when they ended set 1 with it.  UM was really going for it in the new venue and the sound was AWESOME downstairs!  Set 2 continues with a bunch of stuff we havent gotten in a while....Mail Package, resolution wiht great jam from previous halloween, and morning song was beautiful!  Kris Myers was in rock star mode for Mother where he sang and ran all over the stage....awesome start to the weekend!}
\Review{11-01-12}{Calvin Theatre, Northampton, MA, USA}{Jimmymac03}{Amazing show. More amazing than the music though was the set break entertainment. In the second row of (or maybe third) of seats there was a dude peaking hard. He was out of his mind and everyone was enjoying the show. The moment security came by he decided it was good time to drop his pants. Not wanting to touch naked man junk the security and cops actually just let him be for a good while. However, once the second set started I am pretty sure they took him out.}
\Review{12-30-12}{The Tabernacle, Atlanta, GA, USA}{GreatestAmerican}{Incredible night. The energy was through the roof. Was happy to see my friends in UM Nation get down to my boys moon taxi first off. Then Umph blew the tabernacle apart. Rocker was a very special moment in which I was glad to be a part. Whole acoustic "set" very good with great song selections. Second set was hot from the start with bright lights\textgreater \enspace  cocaine\textgreater \enspace  bright lights being a highlight of the weekend. Domino\textgreater \enspace  sine on\textgreater \enspace  domino was a surprising sandwich although it thoroughly delighted this fan.}
\Review{01-18-13}{Beacon Theatre, New York, NY, USA}{dubzz}{I can commiserate with danoc, missed the intro and most of 40's due to tough travels from Boston.  N2F \textgreater \enspace  Ocean Billy was monstrous and well overdue in the past few shows.  There is a great Jake solo to close it out. Although I'm not a tremendous Radiohead fan, those who like them will really enjoy the rare Weird Fishes cover.  Plunger was a great heavy hitter to close the first set.  22 minutes of domination to start the second set with Strings.  The entire follow up was a continual rager.  Wormborg, Wappy, Ex1 w/ sax were wonderful.  Wappy jam was more smooth than too metal. Finally, the Life During Exodus had the crowd going absolute NUTS! Loved the Heads tribute in NY and first replay since it's intro at Milwaukee. Not a huge Booth Love fan myself, but I enjoyed it.  The reprise of Strings was expected and welcomed, great close to their first performance at the Beacon.  Personal Highlights: Wappy \textgreater \enspace  Ex1, LDE}
\Review{01-18-13}{Beacon Theatre, New York, NY, USA}{danoc}{Wasn't able to catch Leave Me Las Vegas due to the fact that NYC cab drivers are idiots, further more...40's Theme immediately grabbed everyones attention to make it clear there was no messing around in the Beacon. Conduit jammed hard got the energy flowing through what was a slow crowd for the most part. Roulette was a good in between song for conduit and NTF. Ocean Billy was fucking killer. 20 minutes or so, Weird Fishes was pretty cool considering they've only played it 4 other times. Good cover, plunger was good way to end the set i prefer the one from the Fillmore on Halloween more. 2nd Set: Puppet String which rocked the house down(unfinished, saw it coming form a while away), the linear put it back together and professor wormbog was really cool, big fan of that. wappy sprayberry was killer, 1st time seeing that and the light show was unreal. Example 1 with the sax was awesome, huge fan of that song. easily the best of the night. Exodus had a ton of energy and really had the beacon freaking out. Booth Love was expected but was very well played, finished by Puppet String. Great show overall...the crowd was sleeping in NYC. not a philly crowd thats for sure UM.}
\Review{01-18-13}{Beacon Theatre, New York, NY, USA}{wanderingsun}{i was in ny working on hurricane sandy. my last day of work was the same day as this show. dropped some cash on a front row ticket to reward myself for 3 months of lonely, crappy work... wound up meeting my now-boyfriend, who was in the second row.   in two weeks, i'm moving to new york to be with him. but first! he's coming to my hometown for the hangout, where we're going to get a prefest um show.. then we're driving to new york together, but stopping into summercamp on the way.  tl;dr this show changed my life.}
\Review{01-19-13}{Fête Ballroom, Providence, RI, USA}{dubzz}{Easily the most intimate setting I've seen UM to date.  The venue was small, packed, and had excellent energy.  Unfortunately, I feel this night was a recovery and intermission between Beacon and Brooklyn Bowl for the band.  The set wasn't nearly as fast paced or rocking as I'd have liked.  However, this isn't to dissuade you from checking it, easily some of the BEST banter of the year no doubt.  Not a Domino Theory fan or Strangers, but both were typical good stuff.  BB opened the Girlfriend's Better as a tribute to Manti T'eo and substituted the lyrics for "I have a girlfriend who doesn't exist." Absolutely hilarious and had the crowd really digging it.  This made the night.  Loved the Dump City then a nice jazz/rock Mulche's to close her out.  The Floyd cover really killed it and the Jimmy had some great improv.  Although Visions of Parin isn't one of my favorites, I really thought they were about to cover Hall \& Oates, really cool key teases by Joella.   Unfortunately, big mishap during an otherwise great Higgins: Stasik's bass amp was thrown into stand by because of power issues.  They managed to recover.  JaJunk made for a great encore: real happy to see they played it for us instead of saving it for Brooklyn!  Highlight: Girlfriend is Better (tribute to Manti T'eo)}
\Review{01-19-13}{Fête Ballroom, Providence, RI, USA}{N2FBoston}{This venue is new and extremely intimate. Holds only 750 people and even that is split between the main floor and a small balcony. The created a very cool vibe that ended up exploding with energy throughout the show.   From the second Umphrey's stepped on the stage you knew it was going to be a special night. They skipped the intro, which seems to be how every show has been starting the past few tours. First set was filled with special moments but the highlights were definitely the jams during Girlfriend is Better and Dump City (Finally got this song! only took 48 shows to hear it). Syncopated, morning song, and ending the set with mulches was a nice touch too.  The 2nd set was monstrous. Straight out the gates, In the flesh through 2nd self is action packed and extremely tight. You could look around the room and just see minds being blown left and right. The jams were incredible! Another brick int he wall, sociable jimmy, and visions, bahhh it was just insane. You will just have to hear to show to understand. Not sure if i've seen them close a show with higgins, but worked out beautifully with a nice dubby jam in the middle.   Jajunk is always great as an encore. It really encompasses everything that is umphreys. On top of that the jam in this version is epic. Stasik goes wild, as does the crowd.   Shenanigans, thats all I can say about this show.}
\Review{02-06-13}{The Venue, Fargo, ND, USA}{cutsman}{This was my first UM experience. It was my introduction into  "jam" culture. Those lights were the most amazing thing I have ever seen. I can not believe I have not been going to festivals my entire life. I have a feeling that this was the perfect venue. It wasn't over crowded and I had the time of my life. I just wish UM was playing the Electric Forest but I am just as excited to see all these other amazing jam bands I have been missing out on. Thank you for such a life changing experience, for reals.}
\Review{02-07-13}{First Avenue, Minneapolis, MN, USA}{FurnDiggity}{This was my 6th year in a row at First Ave and UM. I was a bit bummed they werent playing more than one night, but I knew that the show would not disappoint... And that was for sure the case! I have been an Umphrey's fan for about 7 years now, and I am only in the 30ish range for shows. So I am no veteran by any means, but they are my favorite band. So I was really hoping for a Wizard Burial Ground, I have yet to see it live. I didnt get WBG, but I got 2 of my other favorite songs that I hadnt heard yet... Division! and Miss Tinkle's Overture. I was in awe after both of those were played. Not to mention Nemo was crazy good, as was All In Time and the Triple Wide to close the night out. I hadnt heard UM cover Bowie before, so that was also a highlight for me. I think I say this every time I see Umphrey's, but this was seriously the best show I have seen of them. If not best, easily in my top 3. Great work of you Gents!}
\Review{02-14-13}{The Metropolitan Theatre, Morgantown, WV, USA}{driver}{Wow.  This was a great show at a great little venue.  There was mass confusion about what time the band was actually going on.  Initially it was listed as 8:30, then someone said their was an opener, and then someone said they'd go on at 8:00.  To be safe, we made sure we were in the venue by 8:00, which was great since the band went on pretty promptly at 8:15.    The Theatre was TINY.  Not a bad seat in the whole place, and the balcony looked like it raged hard.  It was also a dry venue, which was a first for me, but no one seemed to mind since security was really chill.  Miss Tinkle's opened really, really strong and kicked off the night in pretty rockin' fashion.  Walletsworth was well done, but I thought the Domino Theory jam stalled a bit and they ended up pulling out of it, thankfully.  Intentions Clear was a jaw dropper with the band taking things down to a trickle while Waful killed all of the lights.  This led into an okay Push the Pig and, as always, a rager of The Floor to close Set I.    Set II opened with a nice Fussy Dutchman and led to an okay Red Tape.  In the Kitchen really got the crowd moving, but I thought the jam was uninspired.  Thin Air was fantastic--maybe the best I've ever heard Joel play.  The Beatles cover was a nice breather and raged the venue pretty good.  Kabump was a TREAT.  The rode the jam for a long time until Stasik finally unplugged and the band ended gently to close a nice Set II.    The Talking Heads cover for an encore was nice, and the Booth Love jam was nasty.    Highlights:  Miss Tinkle's, Intentions Clear, Thin Air, Kabump.    If you get a chance, see the band at this venue.  They did not disappoint.}
\Review{02-14-13}{The Metropolitan Theatre, Morgantown, WV, USA}{danoc}{Morgantown, WV...what an environment for an UMPH's show in mid Feb. Valentine's Day gave all Umphrey's McGee fans a reason for their minds to race of what possibly they could play. Further more Set I: Catshot was a good way to start off the night, into an always welcomed Miss Tinkle's Overture that jammed hard. Walletsworth was a good fit for an emotional crowd. Domino Theory was pretty sick, really went at it. Intentions Clear really set a good mood for the 1st set. Push the Pig wasn't expected at all, but you'll never turn it down. Wasn't the best version but was very fun. The Floor jammed hard as shit once again..not a surprise. A lot of improve and grooviness/rave feel the show was as an overall.   Set II: The Fussy Dutchman, wow...not a single person was not dancing. Joel was pumped up. Not a Red Tape guy but if i had to see one live I suppose it'd be this one. In The Kitchen was a good up lifting mood after a long Red Tape. Good jams, Thin Air was fucking sick. Haven't seen that one yet until now. I Want You was a great cover.. good sing along for a Valentines Day show. Kabump was tiiiiiiiight. 20 minutes or so. Great Home jam.   Encore: Girlfriend is Better was a pretty cool start to an encore, really went hard and was one of the spacier versions of that they play. Booth Love was expected but not as an encore, heard it up at The Beacon a month prior as an encore so that kind of threw me off. But in the end who is going to turn down a Booth Love on such a great Valentines day down in Morgantown?   Great show all in all, very awesome crowd. Pissed they didnt let me down to the main floor but the 2nd level was hectic and went so hard. Worth leaving my girlfriend at home on valentines day for some umph love, FUCK YEA! Thank you everyone for such an amazing show.}
\Review{02-16-13}{The Orpheum Theatre, Madison, WI, USA}{umphalex}{UM had a lot to prove to make this show better than the last time they were at the Orpheum and they did not dissapoint.  Nippletrix into 2nd Self was a nice touch to get the show started with a good vibe.  The puppet string has some really good improv and good length.  Not quite as funky as some versions I've heard but original and good in its own way.  My fiance called the Mantis on this show and is always a nice treat these days to get that, especially the backside of it.  Triple wide is a great version, taking you through peaks and valleys of electronic grooves...All night long had more thump than normal with 3 ppl playing percussion including Jake.  It was my second time getting headphones and snowcones (once before on NYE with Mirro) and its a great jazzy riff.  I love when they put two jams into Resolution and both of them had a reggae - ish theme which was great!!!  Set two was a rager, dancy jajunk, rocker of a slacker, and the set never let go....  Hollywood nights I went absolutely nuts because me and my fiance will be going to do VIP HOLLYWOOD NIGHTS on 3-22 and 3-23 in Hollywood....Its as if they knew we were going by playing it in our hometown of madtown!  Great show...UM in madison never dissapoints!}
\Review{03-23-13}{House of Blues - Sunset Strip, West Hollywood, CA, USA}{umphalex}{The House of Blues on sunset strip is actually really cool on the inside and has pretty amazing sound too!  This night was a serious rager and is my favorite show of 2013 thus far.  This was my 49th show and my first time to ever do the UMVIP, which was really sick...  Got a signed poster included, laminates, soundcheck on Saturday, and a meet and greet with the BAND!!!  Got pic's with all the different band members and everyone was soooooo cool....  As for the second night of Hollywood nights, well their was no shortage of pure unadultered jammin going on!  My first live "there's no crying in mexico" which always gets you in the mood for some dancy fun...And a super jammy bridgeless that goes to a nice place.  Wappy sprayberry was it's usual dance party with a great MJ tease that was funky as hell with a beautiful backside to brigeless.  Wife soup doesn't get played alot anymore and was really nice to see on the west coast, since we are from Madison WI.  The Der bluten kat takes the cake for the first set though...  Both Jake and Brendan taking turns on keys in DBK and also a first time ever great hip hop tune!    Mulche's got taken to a much higher level than normal and had Jake and Brendan facing in on each other battling out sick guitar riffs  Anytime you get DBK and then Divisions in a show you know it'll be a special night.  Divisions has a serious Jimmy Stewart that gives goosebumps, and then followed by a plunger (which usually I dont care for too much) but the plunger contains one of the funkiest grooves I've heard to date....  Hangover gets seriously elevated to an insane jam level and then the triple wide into divisions to end!?!?! Wow, this is one of those shows....  Good encore with some California lyrics in "the song remains the same" to really let people know why UM is the best out there!}
\Review{04-12-13}{The Plaza 'Live' Theatre, Orlando, FL, USA}{snackUMmack}{First off, this was one hell of an umph experience. My friends and i traveled south from PA to see two shows back to back. This being the first out of the two. Starting off a concert to "Drink My Drank" is a great way to grab the crowd's attention. Then transitioning into "Tribute to the Spinal Shaft" which was up beat and funky as fuck. Joel had his time for a keys solo. Good for him! "Conduit" was next and ill always enjoy that badass tune. "Cemetery Walk" was dropped on the Olando crowd, which dropped my jaw. Never thought i would see it live and not only that but to have it swing right into "Slacker" which is a personal favorite. So at this point...Im flipping out. "Miss Tinkles Overture" was played next and thats just up lifting shredding and a solid jam that gets the crowd involved towards the end. A cover slides right into the setlist and it just happens to be Pink Floyd's "Comfortably Numb". Damn. The room's energy was magical. Everybody was in the spirit now. Then ending the set with "Cemetery Walk II", as expected. GREAT first set.         Starting off the second set with "Der Bluten Kat" \textgreater \enspace  "Miami Virtue" \textgreater \enspace  "Der Bluten Kat" was big. During the Inprov of DBK, Waful flips the lights back on the curtains and really bring out the art in his occupation. The dance moves were just pouring out. "In the Kitchen" was next in line. It was not long in duration, but thats fine. Just hearing the tune is good enough for me. Stasik took a nice bass solo after kitchen which was quite impressive. Then they slammed a solid 18 minute "2x2" which was fucking awesome. Great tune :). "1348" was the perfect way to end the set and it was spot on. Drunk singing and hard raging, just the way i like it.   Encore left me speechless. No one can ever deny and well played "Ringo" and well played it was. For the final stretch of the night, the band was getting real funky. Towards the middle of the song they bring back ringo and leave a Kris Myer's signature drum beat playing on where the crowd begins an up roaring WE WANT THE UMPHS chant. the band then reacts and slaps a "Soul Food II" jam and that was so much more than i could ever ask for. My favorite show so far. Give it a listen when you can. Thank you Umphrey's.}
\Review{04-19-13}{House of Blues, Dallas, TX, USA}{Mantisphantis}{Let me tell you why this is the best UM show of 2013, in my opinion. I consider nipple trix my favorite intro. Ive seen it thrice, Chicago, Stl new years, and the first one at summer camp. Love the energy of it and loved the transition into Resolution. Resolution contained a solid amount of improv for a 2013 reso, thoroughly enjoyed it. Pretty much the one lull came during hourglass (it usually does). A nice full 1348 was a treat mid set, as you usually see it ending a set. Morning song was emotional and perfect. Got goosebumps. Rosanna\textgreater \enspace Conduit was great! Bayliss was feelin himself during Rosanna. A nice mulche's with a jazzy mid jam was a perfect way to end an emotional roller coaster of a set. Set 2 kinda speaks for itself. 5 songs, 6 including the second part of AIT. All in time contained a great jam that sorta sounded like Phish's first tube to me. Day Nurse in between was nice. I like day nurse because it brings a weird funky energy into the room every time. I expected them to continue the set into a new song, but out of nowhere Bayliss began to sing All in Time part 2. Another treat because every other time i've seen all in time it's ended a set. The highlight of the night, the Higgins, clocking in at 22 minutes, contained a "Talking in your sleep" jam (By the Romantics) which was weird and fun. There was also a vocal jimmy stewart about 15:00 through. Didn't recognize the lyrics. This was the best higgins i've ever heard. Slacker was solid and contained some stasik gold. Can't you hear me knockin closed out a STELLAR second set with it's usually fun energy. Everyone always appreciates the Stones covers. The encore was freaking perfect. Partyin Peeps\textgreater \enspace Haji. Ahh. Speaks for itself, i think.}
\Review{04-19-13}{House of Blues, Dallas, TX, USA}{the\char`_johnvoss}{Fun, funky show. Rosanna \textgreater \enspace  Conduit was alot of fun.   Stasik got a little too loose during CYHMK, but thats ok considering the amount of jamming throughout the second set. Judging from the written setlist, it looks like that 30+ minute second set opener took a little extra time. I think they cut out Miami Virtue and one other song.   PP \textgreater \enspace  Haji is a classic encore. Doesn't get much better.}
\Review{04-20-13}{Stubb's BBQ, Austin, TX, USA}{the\char`_johnvoss}{Of the two Texas shows this was by far the best, and that is not to discount how good Dallas was. But, I have a feeling that the boys selling out their first Texas gig gave them a warm happy feeling they just couldn't help but show with the music.   The setlist speaks for itself.   LE\textgreater \enspace Deeper\textgreater \enspace UF\textgreater \enspace Jessica was a great combo to round out the middle of the 1st set.   The entire second set was on point. Encore, just as good.   Not alot of real off the cuff jammming, but solid structured jamming throughout. AND A MOTHER EFFING Daft Punk Cover...   JV}
\Review{04-20-13}{Stubb's BBQ, Austin, TX, USA}{N2FBoston}{I wasn't at this show but the song selection is epic! All the jams are very tight and exploratory. Covering the new Daft Punk song is pretty awesome too.  Anyone know what stew/jam/song they are teasing about 7:30 into In The Kitchen? I've definitely heard it before...}
\Review{07-02-13}{"Summerfest" Henry Maier Festival Park, Milwaukee, WI, USA}{umphalex}{One set never sounds all that great anymore before you go, but they always treat summerfest really well and this was no exception.  Big fan of "Le Blitz" as an opener, really gets the UM vibe and crunchy guitar jams rolling....  It's been a long time since we've gotten turn and dub, and this ones jam goes all over the place...its really sick.  Robot world's jimmy takes a darker turn and ends up being some pretty heavy jam.  Out of order is such a great tune and I personally think it should get more play because it is one of those classic UM sounding tunes...Let's dance of course brought the funk vibe and Sinclair on the sax was a nice treat!  Rest of show is awesome as well, but the dear lord in the encore with sprinkling rain really had an impact on the crowd and was one of those beautiful moments.    P.S. Joel announced before the encore that Milwaukee would be treated to year 2 of Halloween at the Riverside, and this year is 3 nights: 10-31 thru 11-2!!!  Thank you UM!  Wisco loves you!}
\Review{08-17-13}{FirstMerit Bank Pavilion at Northerly Island, Chicago, IL, USA}{umphalex}{UM brought the ruckus at this show for sure...Lot of tight improv and jamming going on throughout.  Le Blitz set the tone right off the bat, but the bridgless with jimmy took off to amazing places.  Dear Lord being stuck in between the plunger was a nice twist, and I've never seen this before....(Dear Lord is an amazing song)  Really into the feel and lyrics on No Diablo, and the interplay between Jake and Brendan has a good supertramp-esque feel..  Tribute to the spinal shaft got busted open big time with lots of psychedelic jam, and it's followed with serious versions of conduit and the linear.  Let's Dance had so much sound with both bands being on stage and the horn players too...I think it was about 15 people on stage jammin out some Bowie...Pretty cool stuff!  Any show with 4 Jimmy Stewart's in it is worth listening to in my opinion, and this show packs a punch...}
\Review{11-01-13}{Riverside Theater, Milwaukee, WI, USA}{carmelocorn}{For Friday night, I signed up for Headphones and Snowcones.  It basically cost me \$40 for a pair of headphones that streamed a live audio mix directly from the soundboard to my tympanic membranes.  This was the first time I tried the experience for an entire show and now I’m afraid live music will never sound the same.  These headphones allowed me to tune out the rest of the world so I could get completely lost in the moment.  This type of experience is the reason I am so in love with live music and now I don’t know how I will be able to fully enjoy a show without a set of headphones on. So it goes.  The second set on Friday opened with a DBK club sandwich and contained the night’s only debut mash-up: “The Final Teen Spirit”.  Dramatic synths from Europe’s “The Final Countdown” directly clashed with Nirvana’s grunge classic “Smells Like Teen Spirit”.  The simplicity of mashing only two songs into one seamless tune made this one of the most successful, straightforward mash-up of the weekend.  Brother’s Rage played a smoking after party show on Friday night that featured one of my favorite sit-ins to date.  Jake Cinninger, the other worldly guitarist from Umphrey’s McGee, joined the late night act for a cover of The Grateful Dead’s “Estimated Profit” followed by some spacey improv.  The jam eventually slammed into the sweaty disco tune, “You Should be Dancing” originally by the Bee Gee’s and featured Mr. Barry Brown on vocals.  Needless to say, a legendary dance party erupted among all who attended and continued into the early morning hours.  Originally posted: summercampfestival.com/2013/11/04/mashup/}
\Review{11-02-13}{Riverside Theater, Milwaukee, WI, USA}{carmelocorn}{By the final day of the Halloween run, most of my crew was hurting.  Too much bourbon and beer had our hotel room smelling like the bathroom of a Wisconsin dive bar.  Saturday’s show was sold out but I ended up getting a wristband for the floor, which ended up being completely packed with people.  I was forced to stand behind a guy wearing a huge mushroom head hat and next to a girl that decided to conserve space by grinding on my leg like a dog humping its favorite teddy bear.  As far as Umphrey’s goes, this was definitely their most animated show of the weekend.  Jake and Ryan were all over the place, both musically and physically.  The first set contained an unfinished version of The Police’s “The Bed’s Too Big Without You”, which made me realize that I will probably never get a chance to hear Umphrey’s cover “Walking on the Moon” live.  Also, it’s about time for Umph to tackle ”Man in a Suitcase”.  The final mash-up of the weekend was “Push the Booth Deeper” and it was confusing as hell!  Most of us had no clue what was going on, which song was being played or whether all three originals were being played at the same time.  A friend was able to get a hold of the song’s notes and confirmed the cluster of confusion from which this mash-up was birthed. To be honest, I am still trying to wrap my head around it.  Umphrey’s McGee finally ended the second set on Saturday night by busting out the Metallica rager, “…And Justice for All”, which hadn’t been performed live in over five years.  But the real highlight of the evening was the relentless “Bridgeless” encore.  As the tune progressed, one particular audience member could no longer contain his excitement.  This very dirty looking man ran across the stage without shoes on, only to be tackled by the stage crew in front of the sold out crowd.  It was then rumored that the same wook ended up outside the venue about an hour later going absolutely insane without a single piece of clothing on his body.  And thus, a Halloween weekend full of mash-ups and debauchery came to an end.}
\Review{11-02-13}{Riverside Theater, Milwaukee, WI, USA}{boarder1720}{Cold November nights in Wisconsin and Umphrey’s McGee have always had the ingredients for a magical show. Dating back to 2006 and even further back if you include October the band is always on point this time of year. Add a great theater that Waful crushed and this night was another one of those nights.  I was beyond excited driving up last minute since my last two set Umphrey’s show had been the Bill Graham private show way back in April.   The show opened up with silky smooth Plunger \textgreater \enspace  Much Obliged \textgreater \enspace  Plunger Sammy giving us a nice treat of some older tunes. The drop into M.O. was spot on where the transition in Plunger normally is which lead to funky jam with a raging peak before bouncing back into the end of M.O. and then fading beautifully into the end of Plunger with a Joel lead piano solo. Everything about this sandwiched screamed Umphrey’s McGee, the precisions and execution was flawless.   Next came Higgins with an exceptional jam, Stasik stepped up and leads the way with an infectious groove that everyone built around. Once again the flow in and out of Higgins was superb. This dance party Higgins got followed up by a rare treat in another old tune Sweetness. This leads some very uplifting, graceful improv landing on a rock riff that Jake ends up teasing Rebubula briefly before he shreds his way into funky riffs everyone picks up on and then BOOM! It drops into Comma Later.   No Diablo came next, a song debut at UMBowl earlier this year and only played 5 times prior. I really dig the Supertramp vibe and I’m glad it’s getting played. Finally, the highlight of the show for me closed out the first set with an extended 40’s Theme that included a verse of The Police’s “The Bed’s Too Big Without You”. Once again the MVP of the night, Ryan Stasik stepped up with some Sublime bass effects that had the place going ape shit until it fizzled into The Police which lead to equal excitement from the crowd. The band then slowly grooved back into the end of 40’s and walk off stage leaving us eager with anticipation for set two.   The second started off with another monster rock sandwich in Mantis \textgreater \enspace  Mulche’s Odyssey \textgreater \enspace  Mantis. Mantis is a tune I really wish would get improv all the time but not tonight, however the powerful first verse had the energy flowing from the start and that spilled over into an insanely powerful Mulche’s. Jake was toying with the Who Knows? riff in the rock breakdown but never went into it. Once again they kept a sold out crowd going full force before finishing the tune and ever so carefully segueing back into Mantis.   Following up this huge sandwich was Miami Virtue, the highlight of set two without a doubt. This version clocks in just under 15 minutes, 10 of which is improv and it is really something special. It has a slow intro where Jake walks over and joins Joel on keys and then they proceed to lay down some very tasty layers together. This dark jam is a great example of where everyone comes together and is doing just enough to mesh together something great. As the tempo picks up everything seems to take form and a masterful team effort unfolds. Bayliss really lays down some licks as this builds up before cutting out into some keys and synthesizer where this dark jam sees the light and transpires into a glorious uplifting jam. This jam then quietly fades into the night with a slow segue into a standard JaJunk where yet again Stasik stepped up and laid down some bubbly bass. The band closed out the second with a crowd favorite cover of Metallica’s  “…And Justice For All” which hadn’t seen the light of night in 577 shows. They encored with a standard Bridgeless which I consider a treat since it seems rare to catch a standalone Bridgeless these days, even if it normally creates great improv. A great choice by the band to close out a show that rocked from start to finish.}
\Review{12-29-13}{Fillmore Auditorium, Denver, CO, USA}{teleskiguy}{The Joshua Redman set is a fine example of people describing him as the "7th member of the band." (We all know that Waful is the 7th member, just like Kuroda is the 5th member, but I'm talking music). Just ridiculous musicianship. Joshua Redman on DBK alone is worth the money paid to buy this show.  Speaking of DBK 2nd set opener, Jaden Carlson's sit-in on DBK is a standout, very incredible 12-year-old gal from Boulder holding her own with UM, awe-inspiring to say the least! Listen to Jake yell out "OH YEAH!" at the end of her sit-in!  I effing loved the Plunger Jimmy Stewart, just real raw UM!  River People is one of the sexiest and funkiest things I've heard this band do onstage. I've listened to the first 4 minutes of this song about 30 times now, and I play it for my gal friends to great effect! River People can and should somehow make it into rotation.  Most of my favorite moments of the this NYE run are on this show.}
\Review{02-16-14}{The Fillmore Silver Spring, Silver Spring, MD, USA}{bmrobin}{the band walked onstage to the theme music from House of Cards, which was appropriate considering its Season Two debut the night before. energy was high throughout the first set - resolution\textgreater \enspace conduit was relentless and the liquid\textgreater \enspace den jam was just awesome.   despite rocking out really hard, the band seemed very laid back during the second set which made it very enjoyable. push the pig contained a tease of "Let Me Blow Your Mind" by Eve and had a cool jam with Joel and Jake on keys.}
\Review{04-19-14}{Stubb's BBQ, Austin, TX, USA}{dubzz}{Great close to the spring 2014 tour and what proved to be a heavy handed pimp slap follower to a strong Dallas appetizer.  Not surprisingly, given it was Austin, Joel Cummins and the Frequent Fliers were ready to build a house with the bricks that would be shit this night.  Set I:  The party started with one of the more ominous, bass heavy openers (Le Blitz) in rotation transitioning into the ever dependable 40's.  Improve was sexy and smooth, but, like my penis, short. After we all rock n' reveled in the quantities of beer we were consuming and anticipated the painful anal outpourings of tomorrow, Xanadu Farag windchimed us off into an OoO.  As drums pounded and strings reverberated, I tried to tell my lame Cheese fan friends for the treat they were in for.  Too fucking late, that riff split them accompanied Baylor's lyrical introspections, tearing across the expanses of their synapses with reckless abandon.   The neural carnage was far from over but, alas, respite: The ever reliable Much Obliged.  Dependable for both improvisational consistency and to put a little pep in your step, dare I say funk in your trunk.  If you don't catch a groove on this, you seriously should be evaluated by a doctor to determine whether you are an emotionless replicant android. Started strong building around a nice Pony Bass line, the funky improv was strong with this one.  Couple beat drops later, the crowd was rabid.  It didn't stop there, so begin the strongest three song series of the show.  Recently introduced Final Word has people reaching for the nearest kleenex box under the Waful whites. Great song I've really enjoyed since I first saw it at this past year's scamp and fit perfectly between the MO and, oh look, fucking 2x2.  And you thought it was over, sike motherfucker, time to deep some even deeper personal relationship reflection. Metallesque jam section with some great guitar collaboration.  Standard dance party for BLBC to close a notably impressive trifectum down.  I missed most of this as I was still collecting most of my viscera and appendages off the Stubb's ground post the first set stunner series.  Set II:  The party refused to stop. N2F right off the bat with strong improvisation about 13+ minutes, gradually becomes bluesy before the reprise.  Do recommend.  Mentholated logs were being scorched to calm the souls of the unrepentant, but soon, despite their misdeeds, vindication was assured (see NOT deeper \& ait).   Deeper is a lame song anyway despite this particular one being particularly uninspiring. If you take issue with that, please contact my proctologist, schedule an appointment, and check your ass for a dildo.  Standard AIT to follow, which was amazing regardless.  Crowd was really into it and Waful was on point with his light cues.  Then came the concert magnus opus.  What all the hitch hiking, ticket scalping, and moon rocks were done for: August.  The transcendent lyrical stew that accompanied this song cannot be described effectively with words, only half experienced through sound board quality MP3 turned up to 11 (and by 11, I mean until it feels like there is an F22 flying by your face). The beat from the opening August gradually fades, then those keys, MAN, those keys. Joel starts building this melodic casserole that just turns into a monstrosity of uplifting jamsandwich.  The guitars come in and we start soaring toward the heavens, riding that improv powered bus known as Umphrey's McGreat.  Suddenly a BB angel starts augmenting the ascension with choice improv lyrics. I am crying at this point.  Every sane person is straight up weeping. The crescendo peaks and he simply croons out: "It's not the view that's complicated." Take that and put in your third eye, Phish fan. The lift begins to fade and boom:  "And what I'm trying to say Is its nothing but the view that changes And if I could see above the trees, I wouldn't disagree But I'm not the one who made it complicated."  Then the shreds of your existence are melted away by some godly rifts and pounding of the keys. I'm no man of God but, given that we were literally minutes from Easter morning, this would have been the moment Jesus would have stepped out from behind Chris playing a goddamn keytar if the fucker had any sense.  Or perhaps even better, emerged from Brandon's mouth, bursting through at the highest note of the stew, climbing out like a stripper at a bachelor party. He'd just straight split out of the inhumanely outstretched mouth and be like, "Helluva stew guys, thought I'd say what's up." Of course, BB's mouth would magically restore and we'd all have a mega laugh, until Jesus got hold of our rocks, because you know he's a mooch, man. Or fuck, maybe Andy would just tear off the pubic shag and it turns out he was Jesus the whole time.  Standard Floor.  Great funky Miles Davis company alongside the trombonist from the Mike Dillion Band.  She was fantastic, great energy, and a complete smoke show.  Encore:  Patrick Bateman said it best: "Their early work was a little too new wave for my tastes, but when Sports came out in '83, I think they really came into their own, commercially and artistically. The whole album has a clear, crisp sound, and a new sheen of consummate professionalism that really gives the songs a big boost. He's been compared to Elvis Costello, but I think Huey has a far more bitter, cynical sense of humor."  And by cynical, I mean Heart \& Soul is beyond the cat's meow: its the cat's vagina. Fuck yes.  Bad Friday, sense its debute 12.31.13, has been growing on me, this being my favorite so far.  Fun song with tremendous upside, would bang again.  Summary:  End tour. Easter. 4/20. Austin. Great show, wish you were all there.   Must Listens: MO \textgreater \enspace  FW \textgreater \enspace  2x2 N2F August, August, AUGUST}
\Review{07-05-14}{Red Rocks Amphitheatre, Morrison, CO, USA}{umphalex}{Umphrey's first sell out show at Red Rocks never disappointed throughout the entire evening.  A debut opener was to be expected from such a magical venue and the first sell out which will hopefully bring two nights at the rocks next year.  Melded perfectly into conduit which has a great rock/psychedelic jam to it that reaches a good level and dumps off into a standard version of cut the cable.  Jajunk gets the treatment and ends up being one of my favorite jams of the night.  Joel takes it to another level with the dance infused funk keys, but the entire band is on point and brings jajunk to a place like I've never heard before...   Seamless transition into an always welcomed Ocean Billy which set the tone for the first set and let you know that it was going to be a rager of an evening.  Awesome placement and choice on putting Gents in the jam portion of ocean billy.  Originally an in the kitchen jam which has gotten the Umbowl treatment but I believe was first at the Belly Up in aspen last year.  It has an in and out jam which keeps dumping back and forth and has a great tone.  This is one cranked up All in Time next that has instant classic rocker written all over it.  Midway through the jam in All in Time I can remember thinking that the first set was already nuts and they would be wrapping up the first set after that.  But then we got the always gorgeous notes from Jake playing Jerry's 74 guitar to end of the road.  Educated Guess was an awesome treat to get debuted and was playing in my head throughout the next morning.  Set 2 opens with Jake calling out Kris Myers on the kit and getting right down to it with the second Little Gift which has some good rock qualities that get you in the UM frame of mind.  Bridgeless is where the band starts to jump off and take us into a jam filled evening with fresh takes on everything being played.  Very rock/funk oriented bridgeless that no one wanted to ever end which moves into the funky dance groove of Bad Friday.  Dominic Lalli blows up on Bad Friday and there wasn't a person not dancing in that place.  My second favorite jam of the night came with Dump City...  I went absolutely nuts when I heard the first notes of dump city, and I feel this song should get the treatment way more often!  Very dark oriented space groove that allows the listener to dance but also blast off into a little weirder space.  Slacker has a good jam on it that has Joel offering some really fresh licks on the piano and a good old nostalgic rock and roll feel to it.  Wappy sprayberry offers its typically awesome dance party and it never ceases to amaze me how many different jams they keep putting into this song.  A fitting back side of Jajunk to close out the night and let everyone know how far UM has come as a band and being one of the tightest, if not the tightest, band today.  I couldn't have asked for a more perfect encore being a gigantic Band fan...Ophelia invites some horns out to take a classic look at this classic cover.  Haji has always been a fan favorite and gave me gigantic chills and goosebumps with Brendan's lyrics echoing throughout the rocks.  If that wasn't enough then they made sure to seal a perfect night with the raucous back side of bridgeless that left no one in doubt of how powerful a show this really is.}
\Review{08-08-14}{Hampton Beach Casino Ballroom, Hampton Beach, NH, USA}{Umph1348}{One of the best shows I have seen in 120+.  The energy in that room was off the charts and the band was really feeding off of it.  Such a great setlist of rarities and "non-standard" stuff for a Friday night show.  The improv (particularly the sandwiches that opened each set) is outstanding.  This one holds up well on tape but also has a strong "you had to be there" vibe because of the raucous energy.  One of the most fun live experiences I have had at a show and a soundboard with plenty of replay value.  This is the leader in my clubhouse for show of the year, 2014... 5}
\Review{08-08-14}{Hampton Beach Casino Ballroom, Hampton Beach, NH, USA}{MitchMitchell99}{Of the top 5 list of my favorite UM shows are both times I've seen these guys at Hampton Beach Casino Ballroom. Something about the small stretch of coastline we got in NH seems to bring out the best in people there, for the crowd and band. The Ratdog and Jim Gaffigan shows I saw had performers and crowd alike having a ball. Keeping coming to the beach fellas and bring back Proverbial! Thanks for that, John Scofield and some of the most fun I ever had in my home state that night}
\Review{10-30-14}{The F.M. Kirby Center for the Performing Arts, Wilkes-Barre, PA, USA}{alexholmes}{Review by graceofbordan, posted 05 October 2017 8:55 pm EDT Such an amazing set but it doesnt show above how Eat is :Eat\textgreater \enspace Draconian\textgreater \enspace Eat: i just love these hidden mashup/transitions soo sick  That's because it's not.  This Eat contained one of the building blocks that became Draconian.  It's just a "Jimmy Stewart", much like 4/11/08 DBK isn't DBK\textgreater \enspace Cut The Cables\textgreater \enspace DBK or 9/4/05 3x isn't 3x\textgreater \enspace Spires\textgreater \enspace 3x.  The songs didn't exist yet.}
\Review{11-01-14}{House of Blues, Boston, MA, USA}{pmahon}{Stellar show from first note to the very end of Gulf Stream.  After the night before with the incredible mashups of Halloween, I was not sure what to expect after hearing stuff like All in Time, Ocean Billy, N2F, and the insane opener of 1348/Kitchen.  Cut the Cable got things going fast and then they laid into some of the best jams I have ever heard with The Floor, Higgins and Slacker both awesome highlights of the first set. The Second set started with an unbelievable bridgeless, den, and bridgeless, which was the first 30mins of the set and left the audience stunned.  Kashmir and Pay the Snucka were really strong to end the set and Kashmir in particular were very impressive.  The band was super tight throughout the whole night and after a night of great mashups it was awesome to see them lay into a really strong show full of improv.  This night I also stood a bit further back to appreciate the lights (night before I was rail) and the lights as always are an amazing part of the band.  Waful always does an incredible job and this night was no different.   The encore was incredible and choosing Gulf Stream to close out the weekend was awesome.  After two incredible nights of music and hanging out with the band as part of UmVip, capping off the weekend with Gulf was the best choice they could have made.  It was my first time experiencing Halloween with UM and I look forward to many more shows with them in the near future!! mm/.}
\Review{01-03-15}{The Tabernacle, Atlanta, GA, USA}{thardin}{The first set was stellar. When they played Wappy so early, I knew we were in for a great night of straight UMPHunk! The Bottom Half and Syncopated Strangers were the highlights of the first set even though Led Boots \textgreater \enspace  Mulche's was a great way to end the set.  The second set was priceless! Hands down one of the best sets of music ive ever seen. It wasn't even fair. Every song was perfectly placed. The Dump city and crooked one were of premium quality. Perfect night for a flawless show.   The encore took me back to my childhood and i couldnt help but boot scoot boogie. Best UMPH show yet for me!}
\Review{01-30-15}{Taft Theatre, Cincinnati, OH, USA}{TheLinearLawyer}{This show was a high-energy jam fest right from the start. Fir, Divisions, August, and Dump City were particularly inspired. The Puppet String freak out \textgreater \enspace  the end of Bridgeless brought the house down, and Bayliss absolutely nailed "Sledgehammer." I give it a 9.2 out of 10.}
\Review{02-06-15}{Ryman Auditorium, Nashville, TN, USA}{WappyStrings28}{If only there were words to describe this night. Easily the best setlist I have ever seen or heard live, Puppet String and Rocker 2 are some of the best jams I've heard possibly ever. Not to mention the 6 first set rarities.   I Want You (She's So Heavy) nearly caused the Ryman to crumble to do the energy in the room. The crowd was into it from note one. Not to mention the first ever and absolutely incredible Rocker, Rocker 2 combo.  Second set is near perfection, whether it's improv or standard songs the placement and execution of everything is seriously A+ stuff. All In Time encore featured the latest "Cigarette Cables" lyrical stew.   This was seriously one of the best shows I have ever seen, the room was insane and the energy was indescribable. Very thankful to have been in attendance. 7}
\Review{02-18-15}{Calvin Theatre, Northampton, MA, USA}{Umph1348}{Outstanding show last night.  I guess that is to be expected as UM is batting 1.000 at The Calvin.  Some of my friends were sort of "meh" on the first set, but I disagree.  Set one was bookended by two great pieces of improv in Fir and The Haunt.  I was ecstatic to get both of those tunes in the same set.  Admittedly the middle of the set (while well played) didn't pack the punch that the rest of the show did.  The Nemo/AD sandwich was well executed but most of us diehard fans would have preferred a jam in Nemo in place of Anchor Drops, c'est la vie.  I don't love Deeper, but the ethereal jam that came out of it was nice.  A standard Billy was cut short by Bayliss on the talkback mics.  This was a great move IMO as it allowed for The Haunt to really have room to stretch its legs.  Jake was all over the Haunt jam conducting the band and being the mad stork that he can be up on stage.  Truly a frenetic and awesome Haunt jam, I hope that it holds up on tape.  While set one was "good solid Umphrey's," set two was the stuff that makes me keep seeing these guys and makes it easy to provide an answer when asked:  "who is your favorite band?"  The Preamble fakeout into JaJunk was a nice twist and the JaJunk jam absolutely crushed.  We were in for a real throwdown in set two as something clicked onstage and we were to treated incredibly compelling improv over the rest of the set.  JaJunk, MO, LMS, BLBC and Sociable Jimmy ALL had great jams in them.  I need a relisten to opine on Brendan's lyrical stew out of Much Obliged but every jam in set two delivered.  There was a"middle eastern metal" (a section played during a past UMBowl S2 quarter) jam coming out of Last Man Swerving that was one of several highights in the set.  I have been fortunate over the past few years to catch some 99th percentile UM shows (10/29/14, 8/8/14, 10/18/12 and 4/28/12 are good examples) and honestly I am not sure I have seen a better and more interesting set than set two last night.  I should probably wait for the afterglow to wear off or to at least have a relisten via the UMlive app, but frankly I don't need it.  What an awesome set of music.  The Soul Food II\textgreater \enspace Soul Food I\textgreater \enspace end of Mantis encore was just icing on the proverbial cake (I also thought I head some Bad Poker teases from Jake in SFI but will need to confirm).  There aren't enough superlatives to describe just how great last night's show (with emphasis on the second set) was.  The song selection was also incredible.  To get two highly sought after rarities like The Haunt and Last Man Swerving in the same show is enough of a treat in and of itself.  One thing that is notable is that there weren't any tunes from Similar Skin played (this also happened on 10/29/14) and that was somewhat refreshing.  While I love the SS material, gettting a "rest" from some of the songs that have been in heavy rotation since the album dropped helped to enhance the flow of the setlist/show.  This is not a critique of SS or the frequency with which some of those tunes are played, just an observation.  Folks who are looking for a sterling example of what UM is capable of would do well to check this show out.  It was special.}
\Review{02-19-15}{State Theatre, Portland, ME, USA}{ohmykai}{After weeks of being snowed in, we made the ride to Portland.  Word was the Couch Tour stream unable to happen, there was a full blown snow squall at doors open with near white-out conditions that made it an adventure right up to the gate.. and the room energy was certainly high as the audience trickled in from the cold wind and snow. Tauk opened. My first time hearing those guys live and it was a great experience that drew in those cold feet for the first round of dancing. I'll focus on UM here though.  Set I. While the room sound is not the greatest at the State, a little boomy at best, the music was excellent. Most of first set was spent in the balcony. All of second set was spent grooving on the Goldside. Listening back to the umlive version now, it starts out very energetic. A nice Drink My Drank into The Floor. Divisions takes off, drops a mad drum jam in the midst and finds it way off to a smooth Stanton (2nd time played). After dancing around that theme they return back to Divisions for a good wrap-up with some nice belts from Brendan.   My personal feeling at this point is the band feels like the eyes of the world are off them a bit. Stream is cut off, no one but us is watching. They aren't rushing and its very electrified. The band is beaming. I like it. Mulche's Odyssey kicks off with some tight energy and is another example of some of the wild execution they nail tonight. Yet again, frenetic pace but patiently done. The mid-song groove is heavy and dirty, gives way to the main theme, and drops into a pleasant funk zone that is peppered with some nice spacey, padded out jams. Doesn't take long for the night's abundant energy to come back either! Back on the Mulche's theme proper, and I'd just say listen. This speaks for itself. Umphrey's is doing exactly what they do best and it is certainly a stand out moment of the first set for me. Short breather, and we get to the nights first Similar Skin offerings.  The Linear starts out strong, solid version. Vocals are on point, Jake peppers the lines with some fun guitar work throughout. The bottom drops out, we fall into a very ambient zone. Getting that sensation again that we're a cut off from the world. Guitar gently teases the chords to Cut The Cable and there it is. Tight playing, great vocals. Really dug this! Short and to the point. Another pretty decent pause. Again not feeling any sense of being rushed in this! They pull out October Rain and it is thoughtful and precise from the get go. I haven't heard this song live, and was impressed with its styling. Quick breath and we drop into Live and Let Live. Solid version, strong playing throughout. Nice way to end a strong set with some familiar tunes and some I'd never seen played live before. Notable songs for me were Mulche's, October Rain, Live and Let live.  Set II begins with Bridgeless and is a solid rocking opener for the later night. Vocals are good, playing tight as well. There is no sense they lost that pace from first set. A punctuated jam space gives way to Hang Up Your Hang Ups another second time played offering. Nothing lacking in this song either, and the band plays on through a few iterations with an intense Joel driven segment near the end. Feel like getting in the van? Yes Brendan, we do. Get in the Van is solid, executed flawlessly. After a ride around Portland in the van, we park ourselves back under the Bridgeless. The intense high-speed chase that is the end of Bridgeless runs wonderfully and well.   "This one's for you, Joel." Counterpoint to the set start in pocket, FF rises from the mid-set fire - a gift from Brendan to Joel - which is wrapped to suit in execution that's defined the show overall. Tight, energetic, and very fun to dance to. Darker themes begin to play the end of FF with a return to some deep ambiance. We drop into Made to Measure. This song follows the trend of an night full of great offerings. Some really cool guitar work accompany the stomping piano lines, with vocals from the band on par with the music. We're never ever slowing down, and when we hit groove time it's unique and rhythmically piano driven. I'm beginning to really dig the prominent Joel tonight. Lose yourself teases and a smooth hip hop element round out the end of Made to Measure before rocketing off into 40's Theme back to an absolutely electric pace. 40's Theme never fails to deliver for me, and this is no different. Well done, and totally jammin'. The texture turns smooth and funky as the song progresses. Bit of a breather again, compared to the rest of set II!   The band introductions go 'round and a little Game of Thrones theme comes out before we hit the End of the Road. Sweetly played, with some arrangement much unlike the studio version. Definitely a cool space presented here that rolls nicely into Roulette. Roulette carries on with the nice execution of the night. Good vocal harmonies over the verses. "Question is, are you guys read to rock?" Slacker jumps and jams its way to the close of set II. Great version, and very lively! It builds to an excellent crescendo that doesn't want to quit. Now they've played a few great gigs in Portland in past years though this may well be an example of the best they've given us so far in my opinion. A combination of a very choice set list and top notch execution throughout. Notable songs for set II were Made To Measure, 40's Theme, and Slacker.   Encore: The Triple Wide. A favorite of mine, and what can be said that hasn't already been said about this one. Just as good as the rest of the show, and a fitting close to a great night.}
\Review{03-19-15}{Crystal Ballroom, Portland, OR, USA}{spaceoutintime}{Right up front, this was my first Umphrey's McGee show. Holy guacamole. Most likely you know the rest of the story. First set was offdahook. Miami Virtue, Ja Junk\textgreater \enspace ...\textgreater \enspace ...\textgreater \enspace JA Junk sandwich. Followed by a scorching second set without nary a throwaway either. These guys are the real shiznit.}
\Review{03-20-15}{Crystal Ballroom, Portland, OR, USA}{spaceoutintime}{Maybe not at quiet the same level of energy and magic as the night before, but this was still one heck of a dance party and good time. A juicy Mantis sandwich in the second set containing the most unforgettable, accurate, and powerful cover of the Pixies' "Where Is My Mind?" I have ever encountered (Patrick rocked the Casbah!).  Then to top it off, the Radiohead/Beck/Phil Collins mash-up for an encore had to be seen/heard to believe. I can no longer resist the momentum of this music.}
\Review{04-25-15}{First Avenue, Minneapolis, MN, USA}{tunafist}{Great show, saw them Friday too, and this was my first time seeing them this year.  Great rapport with crowd and very high energy, they also played a fantastic mix for veteran fans as well as newbies.  Saw my first Moccasin!!!  Another great set of shows that solidified my belief that this band gives you a show truly unlike any other!  m/}
\Review{07-16-15}{Blue Hills Bank Pavilion, Boston, MA, USA}{pmahon}{First off, great show, just wish it was longer.  Lettuce was a cool opening act, however, not many were there to enjoy it unfortunately. Because of the co-headline, they got a shorter set but they got right to work.  Junk was solid right out of the gate, and the bottom\textgreater \enspace anchor\textgreater \enspace linear\textgreater \enspace non-compliance was great.  They have not played non-compliance alot, which is a shame cause it has a sweet riff and a top 5 stew song for me.  Plunger was a weird kinda funky different jam, and clearly pretty good as it landed on the HOF 2015.  The rest of the set was great too, nothing crazy, but great songs with solid jams throughout.  The encore for me, made the show.  Booth Love with the Eminence jam into DBK was so cool.  Haji is always great and the back half of DBK finished off a truly solid night for the guys.  Cheers.}
\Review{07-17-15}{Stone Pony Summerstage, Asbury Park, NJ, USA}{Paytheslacker}{I'll attempt a full review later, after some sleep from this epic weekend (just got back to NYC from Baltimore).  But I will say that there was a Bulls On Parade jam during Conduit, about 6:30 they begin to tease it for a minute until Kris comes in with the vocals and the full out jam, until 9:12 when they come back into Conduit.}
\Review{08-13-15}{Iroquois Amphitheater, Louisville, KY, USA}{ontheclockdumps}{Man, where to start... First set while rather a "slow start" was still an amazing group of tunes.  The power outage sucked, but i think the band made up for it with the stew that made a rather boring Educated Guesses a monumental rawk piece. The second set started off with a bang and failed to slow down.  If that tinkles doesn't get at least an honorable mention for HOF, then I don't know what does.  This show is worth a listen or two, check it out, overall would give it a 7.5-8/10}
\Review{08-20-15}{The Fillmore, Charlotte, NC, USA}{prdesign}{Chris Mitchel's 500th show and he was the set list writer this night.  The show starts strong and just gets stronger to the end.  The show is along Umphrey's harder, heavier, darker side, with a little bit of dance party added in for good measure.  Songs ranging from the early umph catalog to the most current.   five stars or how ever you want to rate it.   It melts your face.}
\Review{10-26-15}{Georgia Theatre, Athens, GA, USA}{MusicIsLife}{Let me start by saying that I flew from Toronto, Ontario Canada to see both nights at the Georgia Theatre. The extra money I spent to fly in was so worth it!  The Gurgle opener was a perfect call in my opinion. The anticipation you could feel in the crowd reached its peak. House Lights came off and BAM! They came out like yeah WHAT'S UP! The Push the Pig had all the fatness of Waa and bass you may have come to expect. They get better every time. The lights added to the enjoyment of the song and  then with very little pause Jake starts a solo (masterfully precise as per usual) that lead into a wicked Soul Food I could not believe what was going to come up. The Similar Skin to follow got everybody in the place jumping. It was packed! Everybody was having a good time, rocking out sharing smokeables in various forms. The energy you feel  when you see them perform the songs that just connect with you is whats unforgettable about the live show. When you hear the studio tracks and think How? TO SEE IT ALL HAPPEN mind blowing. These guys are just super tight. Have set up hand signals for changes and always listen to each other. The crowd was cheering so much I have to download the live shows to hear what Joel Brendan Jake and Ryan were saying because I cant be sure. The ALL THINGS NINJA fucking loved it. I did hear Brendan say it was someones 250th show and you that you dont always give them what they want you gotta give em what they need. Man did I need to hear that track. After that show I realized there was a hole in my All Things Ninja T-Shirt but I wore it. So that was awesome. The All in Time\textgreater \enspace Mad Love was unexpected, amazing , beautiful, awesome.... Again shout out to the light show because it really added to the amazingness of the composition of their songs. Set break must beer and more smokeables exchanged. Set 2  The Floor best version I've heard but that was like the 4th time for me so although very good I was hoping for an epic tease that never came. 2x2-What YES! That's all I had to say. Took me minute to recognize the part of No More Tears that was teased. RESPECT. Cannot say enough about the talent that is possessed in every member of this band. Just when you think there might be one that overshadows another in the band they show you how well they play as a hole. Every member is essential to their consistently mind blowing shows.  The Bad Friday was sick! Loved it. Nuff said. The Haji was amazing\textgreater \enspace  All in time again. A bit of Georgia Love I guess reaching back to the Tabernackle run... but I liked it better because I was there for this one. Again seeing it live 100x better than blasting it in your headphones. If memory serves the Hangover had  a little Break Out The Booty Wags (ITS MONDAY NIGHT!) Epic. Tickles-5th time best time. Come Closer not seen since encore night 2 summercamp '08.  That gave me flashbacks.  Masterful Show.}
\Review{10-27-15}{Georgia Theatre, Athens, GA, USA}{MusicIsLife}{You'll have to forgive the spelling mistakes in my review of night one. Seems I can't edit it. Night 2. Any  consecutive show  we should all remember  3 simple rules. Rage. Rest. Repeat. I mean REPEAT night 2 was  just more enjoyable. Found company with people I met night one and when you make new friends its always a better show.   Didn't know what to expect given what was done to my brain night 1. Shout out to Brendan Joel Chris Andy Ryan  and Jake  who didn't get enough love. One weird thing I realized no Joel Chant night 1... The slack was picked up night 2 but lets start with the Preamble. Nice! 1st time seeing it but you always know that Mantis is going to follow. But we got the Mantis Ghets, Mantis 2/3rds. But it was the greatest 2/3rds I've heard and experienced. I saw them playing it all singing and I was singing along, although not as well.  All I can say is when you remember what a Song is like after seeing it live you develop a deeper connection with that song. I have a new appreciation for mantis. Moving on. Alexs House... everyone was groovin'out to the light show I'm pretty sure that its rare. So I felt lucky. But it went into  40's! JAKE THREW IT DOWN that was hype. ABSOULUTELY NO ONE IN THIS BAND IS A SLOUCH Brendan was solid, Joel was steady. Chris is always mystifying to me. He's the hardest working guy and the quietest, well him and Andy. Andy is the essential percussive support that really helps fill the gaps. Ryan's usally good for 1 thing to the crowd. Night 1 was I think you guys are the loudest crowd ever. Wicked version. Moving on Example 1 with Demolition Man tease(so cool) was not only good transition musically in my opinion kept the vibe going. I remember that Brendan and Jake brought out the 2 custom really block looking guitars for this they seemed to have fun playing them and the sound was good but, not as good as their regular guitars. I had no clue what to expect next. Then, Room To Breathe AAAHH so good.  Only to be followed up by a No Diablo that really hit home with the crowd and took the vibe to 11.  The In the Black was super impressive because it went straight into Mantis end set 1. I had to pee since Mantis so I booked it to the bathroom and then bought more beer.  Set 2 You see what happens when you chant Joel. Divisions opener. Divisions is a great song. One of my favourites. But I was honestly glad it was played right away. The Roundabout tease was unexpected and 100\% awesome. Dump City was SO GOOD but people kept asking me what song it was and that sucked.  Little Gift never heard before it was a beautifully written song. INTO SLACKER What! Boosh! Totally into it.  I think this was when the Joel Chant happened then Conduit. It might have been after Conduit but I remember the chant and partaking in its glory. JOEL, JOEL JOEL JOEL JOEL JOEL JOEL I also remember Brendan saying Do you see what happens when you chant Joel. LIFE DURING EXODUS IS WHAT HAPPENS with a wicked Fleetwood Mac tease(Riannon )and a 1348 encore is what happens! So epic.  I hope I never lose my memories of these 2 nights at the Georgia Theatre.}
\Review{01-21-16}{Beacon Theatre, New York, NY, USA}{MusicIsLife}{10th show 18th B-Day Show for Umph. Goonville was cool. I never know where the created openers lead but to have it drop into Plunger was awesome. I will give nothing away but, the Banter in this show between the band and the crowd is priceless. 40's was good as usual. "Pick up a couple a New York City 40s"  In the Black was solid. Better than Athens I thought.  Roulette was totally a highlight. Unexpected and always welcome; but to have that go into Kimble!! SO SICK. My buddy wants to dick punch me for that one. Attachments newer song, great song. 1st time I've heard it live. The Rocker Part 2 filled out the monster and as always a great way to end set.  Irreplaceable.    All in Time- Having heard it broken up in Athens; to hear it start to finish was just what the doctor ordered. Crowd. Hyped.  Knew something got teased wasn't sure what but to find out Kris pulled out the end... Very cool. Booth Love I heard this home in Toronto in 2011 when they played the MOD Club. This one was waaay better! Plus the you belong to the city tease and priceless banter from Jake. Wicked. I'm thinking push the tempo up and the next song they pull out is Bridgeless! Yes! Unfinished jammed into Remind Me. Nicely done boys! The tribute to spinal shaft was just rockin' best one yet. It had the Xxplosive tease and Jake played around a bit with the strumming but it wasn't Still Dre like a few dudes in front of me thought. Rather than educate I felt they would figure it out later. BOOSH back into Bridgeless, Ryan was killing it. End set.  Encore Space Oddity \textgreater \enspace Fame. I thought wicked Bowie tribute and the mashup was unexpected and awesome! So happy to have been apart of UM history.}
\Review{02-13-16}{The National, Richmond, VA, USA}{DBONES}{This was a pretty kick ass show. Phil's Farm has a great jam and then Great American has a sweet jam that kind of sounds like an alternate version of the jam on Phil's. 2x2 is always a treat. They slayed both parts of N2F, as usual, and the Stewart with vocals on Plunger will make a cool song someday. It doesn't rage but Jake shows off some of his finesse on the strings taking some beautiful solos. HBB is a beast to end it with a Joel heavy atmospheric jam.}
\Review{03-24-16}{Harrah’s Lake Tahoe South Shore Room, Stateline, NV, USA}{fractalmoe}{This show is incredible.  Both first and second sets have character.  I was stoked to hear In The Black live for the first time, I think this song is one of their best yet and can't wait to hear it recorded in the studio.  2nd Self and Utopian Fir are both Hall of Fame worthy.  I've never seen an UM crowd so fired up than during the Utopian Fir jam -- the entire place was bouncing like it was a god damned rave... it was a beautiful thing to be a part of.  The second set Cemetery Walk sandwich is delicious.  It really pulls the whole thing together and the CW II ending is one of the most incredible musicial moments I've ever seen live -- Waful deserves some credit here too because the synchronicity between the band and the lighting at the end of that song was surreal.    Farag singing Dirty Love was fun and perhaps a foreshadowing of the Arthur Barrow sit-in that took place two days later at the Wiltern in LA.  Encore was meaty and satisfying, Andy's Last Beer being the spinner.  Nothing short of an amazing show here.  Tahoe represent!}
\Review{03-25-16}{The Fox Theater, Oakland, CA, USA}{spaceoutintime}{Among this particular west coast run, from Sandpoint, IDaHO, to The City of Angels: purring galore went down, catnip was fresh and organic, and -- (this night!) -- to my furry ears, was the cat's meow. First set, contender for favorite of the 10; set two is strong throughout but somewhat front loaded. Minor quibble for such high caliber executions unfolding as a single point of boundary dissolving music.}
\Review{04-06-16}{The Lyric, Oxford, MS, USA}{spaceoutintime}{I just finished listening to this show, two days after the fact, in three different sittings.  But wow, even remotely, audio only, with interruptions, this show shines. Liquid velvety smoothness throughout. They were locked in from note one and feeling good. The first five songs (of a six song first set) flow effortlessly into one other, with Mad Love tacked on for good measure. I'm always a sucker for Miami Virtue, as it so often lends itself as a pliable launching pad, and this excursion is top notch. Set 2 keeps the flow going with many high water marks. Everything in it's right place. Their playing this night is inspired and relaxed. Great start to this year's Southern run.}
\Review{08-06-16}{Iroquois Amphitheater, Louisville, KY, USA}{funklewally1}{This was my first UM show. A buddy told me I had to come with him and his crew. He had introduced me to UM previously and I had seen a few couch tour shows, but to be honest I wasn't totally sold...that was soon to change. At the time I was a 90s hip-hop fan so when they busted out a Regulate during the encore I instantly know that this was the band for me! I'll never forget my first Phil's Farm, Wappy, and Kitchen.}
\Review{08-12-16}{Blue Hills Bank Pavilion, Boston, MA, USA}{RobLA16}{First time UM concert goer impressions.  First impressions. I don’t know HOW they remember how all their songs go. It’s like Homer telling the Odyssey. Super impressive. Brendan and Jake. You are the dynamic fulcrum of the band. Jake is the unapproachable guitar wizard and Brendan is the friendly, compassionate frontman. They are the heart and soul of the band. and enhance each other. Big tumbs up to Ryan (nice Celtics jersey), Kris (nice vocal on I Got Love), Joel (beautiful keyboard break, esp during Gents) and Andy (or was it you on I Got Love). It’s one thing for one performer to be able to do it, but to have all 6 locked in, plus the Shady Horns (nice breakdown on Bad Friday), is unique.   Likes  1 Best song of the night for me was Gents, the opener. As a newbie this was sort of the pu pu platter of the UM experience. Everyone gets a little light under the sun.  2 I Got Love - which i didn’t know at the time (Nate Dogg) was a good inclusion. And it makes me think, their covers are pretty much gonna be confined to songs by acts that are no longer really doing it. I like that. So who else did west coast rap in Boston in 2016? I like that.  3 Bad Friday - Yes we all watch Around the horn, so you couldn’t go wrong. And it was a hot nasty Friday in Boston in front of a wilted, lackluster audience. The Shady Horns got to stretch out during this one too.  4 The guy who yelled “Free Tom Brady” right before Wizard Burial Ground.   Dislikes  1 Sorry but I was REALLY hoping for Glory. It had been 6 shows, and I thought it was due. But that’s just me. High hopes low expectations. Having said that…Glory is nothing short of a 21st century classic rock CLASSIC. The whole world should get to hear this song. Truly remarkable and truly one of a KIND.   2 The weather was horrible and sticky and like I said, and it was the end of a long Augist week. The audience seemed pretty wilted. And the band seemed a bit frustrated with that. Or maybe I’m projecting. And they took it out on the music. Hard and heavy all night. Very few light moments. Not a lot of smiling.   Suggestions  Fun to be Happy - Love Tractor. Listen to it, learn it, play it live. It’s perfect for UM.   PS Brown Sabbath was GREAT for the 18 or 19 of us who were there in time to see them.}
\Review{02-02-17}{20 Monroe Live, Grand Rapids, MI, USA}{thardin}{Great show! The set list doesn't do this show justice. The rendition of Night  Nurse is the best version I've personally heard. An incredible Visions \textgreater \enspace  Ain't proud to beg(1,241 show gap)  \textgreater \enspace  Red Tape to close the first. Soul Food I, II and just the second Soul Food III ever played and what a great and fun way to open the 2nd set red hot. I always love a decent Conduit followed by Comfortably Numb which is covered in solid UM fashion. 15+ min JaJunk to close the second! Kimble is one of my all time favorites and is always welcomed especially for an encore. Gulf Stream ends the show perfectly! One of the better shows of Winter Tour 2017.}
\Review{02-02-17}{20 Monroe Live, Grand Rapids, MI, USA}{thardin}{Great show! The set list doesn't do this show justice. The rendition of Night  Nurse is the best version I've personally heard. An incredible Visions \textgreater \enspace  Ain't proud to beg(1,241 show gap)  \textgreater \enspace  Red Tape to close the first. Soul Food I, II and just the second Soul Food III ever played and what a great and fun way to open the 2nd set red hot. I always love a decent Conduit followed by Comfortably Numb which is covered in solid UM fashion. 15+ min JaJunk to close the second! Kimble is one of my all time favorites and is always welcomed especially for an encore. Gulf Stream ends the show perfectly! One of the better shows of Winter Tour 2017.}
\Review{03-02-17}{The Hive, Sandpoint, ID, USA}{spaceoutintime}{The Sandpoint shows were special, but this one in particular fulfilled all expectations, and then some.   An 18-minute opening Conduit with not one but two extended yams? Check. A five-song first set? Check. A songlist show? Check. An incredibly small, intimate venue with superb sound in a breathtakingly beautiful corner of this troubled planet? Check.   By set break, I was already satiated up to my eyeballs. And yet as such things go, I was still jonesing for more (never enough Umph!).   And as amazing as the first set was, the best was somehow still to come.    The second set is an amazing creation of perfect symmetry.  The first three songs flow seamlessly (with Jake playing none other than Jerry Garcia's infamous Travis Bean 500 guitar!) into a long sought after Search 4 hinging into another continuous three-song tryptic of sonic wonder, and possibly my favorite combined moment of this show -- which already runneth over with riches.  Which is to say that ITK- \textgreater \enspace  No Comment \textgreater \enspace  Rock the Casbah is the Real Deal.  One heck of a party that.   And for good measure, the Plunger/ITK/Plunger sandwich encore sent us spinning out into the snowy night still dancing a perma-grin jig.    All in all, this show has it all.  Perfect on-the-fly song selection, execution, and exploration.  Could not have asked for more.}
\Review{04-01-17}{Riverside Theater, Milwaukee, WI, USA}{latetotheparty}{This was my first UM show. I am still blown away by the night we had. Such positive energy from the crowd and the band. If you're looking for technical info about the songs, sorry. As it was my first show I can't compare it to anything. It felt like full throttle all night to me. I guess the rumors are true. UM are good. I enjoyed \#5 a lot and pretty much the second set in it's entirety was madness. It felt like eating a bowl of  asparagus tips. No stalks to chew through.}
\Review{04-19-17}{Cain's Ballroom, Tulsa, OK, USA}{Twisthem488}{Standing in front of me is a girl in a tank top and an Umphrey's McGee hat. She keeps flirting with her boyfriend and and egging on her two sisters with a very attractive level of spunk that perfectly represents the ballrooms atmosphere. Every breath I inhale smells of weed and every visage of the crowd full is smiles. As I watch I see rock bulls made of hands shoot bolts of energy straight into the band. They are 15 feet away. Close enough to catch their eye and close for them to catch mine. Another moment of eyes locked and I'm not just an observer; my level of the enjoyment feeds right back into the music and powers the ballroom. Everyone here is a a part of a larger organism that seeps into the soul. Lights blaze and colorful angel-rays pour through the mist. Who knew heaven was full of rainbows. The music gets louder and the bassist looks as if he's been reborn. I feel his music in my chest and wonder what it would be like to have two hearts beating, pounding at my ribs, and telling me it's time to move, but I think I already know.}
\Review{05-19-17}{Pier Six Pavilion, Baltimore, MD, USA}{bornxeyed}{They won me over. Long time Dead/Phish head here and this was my first UM show...hard to believe after all these years of hearing about them, and even listening to a few shows here and there. But here we are...at Pier Six on a chill night that saw a break in the weather.   My wife and I rolled in and had an awesome time. First set had me hooked. The searing guitar work got me. That Higgins was awesome with the Thunderstruck jam. Then they sink into the Beatles' tune. Grand stuff.   The 2nd set was a dance party through and through. We moved seats at set break and by mid-set found ourselves surrounded by a bunch of younger UM fans, clearly in step with each other. They were having a blast.   Not knowing the songs and the music was a blessing. We had no expectations and left awestruck. Sick show for my money; not sure how it stacks up to seasoned fans' opinions. Met some awesome folks though and look forward to more UM every chance I get.}
\Review{07-08-17}{Levitate Music Festival, Marshfield, MA, USA}{pragmatist38}{I was hoping for Attachments, and they opened with it. Who picked this set list? It was as if the guys were anticipating a lot of people who hadn't seen them before and decided to give them a potpourri- Puppet String, Nemo, Ringo, Higgins, AIT (of course!), Glory, 1348 and Baba O'Reilly? Quite something. And some of the most creative phrasing I've heard from Brendan. Is he getting better? Scary thought... Threatening skies, but not a drop of rain until they left the stage- as if Heaven were on their side...}
\Review{07-23-17}{CEFCU Center Stage at The Landing, Peoria, IL, USA}{pjdwyer}{I know as of this review that Eat doesn't show that they teased Footsteps by Pearl Jam, but they did from about 1:30-3:30. I know that guitar riff anywhere.  Fantastic show. The guys were locked in and ready to play. Absolutely worth the drive back and forth from Chicago and the lack of sleep that resulted. Cant believe I got to see them cover COCHISE! One of my favorite songs ever by any band. Onward \& Upward, All Things Ninja, Kula, and the fantastic Out of Order closer were my highlights.}
\Review{08-10-17}{"Major Rager Charlotte" Symphony Park at SouthPark Mall, Charlotte, NC, USA}{StonedJackBalla}{Great show. First set was real magic. Second set was a heater. Ringo was on point, jam started off slow and teased so hard....then they just let it rip. Highlight of the show for me for sure. . Partyin peeps was a nice surprise. And the 40s encore was pure sex.   Also on another note....city of tiny lites is part of the life during exodus mashup. So it's on there bubba}
\Review{08-10-17}{"Major Rager Charlotte" Symphony Park at SouthPark Mall, Charlotte, NC, USA}{Nicky\char`_Mescalini}{OK, 1st off, this show was fantastic.  One highlight for me was playing a song by one of my all time favorites - FRANK ZAPPA -yeah im an old man :).  UM played a great version of City of Tiny Lites.   However, when I look at the setlist here, it is not listed at all.  Also, in the Song archives, it is stated that it was only played by UM one time --  12 years ago!   Now, no one believes me when I tell them that they played it (that was not at the show) - please get these facts updated on the site - Thank You!!!!}
\Review{09-01-17}{The Pageant, St. Louis, MO, USA}{pjdwyer}{Drove down from Chicago just for this bad boy and then drove back up the next morning for North Coast Festival. Love this venue immediately. Great sound, great crowd, excellent beer section, clean bathrooms, plenty of room to move around.  What a burner. A Bridgeless for the ages. The Utopian \textgreater \enspace  Night Nurse \textgreater \enspace  Utopian \textgreater \enspace  Kashmir is peak Umphrey's for me. Cap it off with a spirited Gulf Stream and the end of Bridgeless was a perfect encore.   Overall just a really fantastic show.  Really glad I decided to go for it. Brought 2 virgins to the show and they both loved it and said they'd absolutely go back next time they come around.}
\Review{10-28-17}{Palace Theatre, St. Paul, MN, USA}{username}{Great Show! Too bad you can't stream on a Roku with the Cleeng service. It took my whole Sunday to get a refund. I'm still getting e-mails from them. They keep telling me that they only take money and "protect" the stream. Not once do they take any responsibility. They say they are not the organizer, nor responsible. What BS!!! When the Roku channel has their name on it, and their name on the bill. The band needs to break away from this shady Cleeng. Whats funny is the band did their job, the streaming crew did their job( It works on a laptop), but yet the Cleeng channel doesn't work. A device built for streaming doesn't work. I guess they think my laptop is the best way to view and listen to music, not my T.V. and high end audio equipment. I can't wait until the band drops this client and moves to a platform like Nugs that actually works.}
\Review{01-20-18}{Beacon Theatre, New York, NY, USA}{DBONES}{This show had some of the most dark and fire jams I've ever heard from UM. They brought out the Snarky Puppy horn players for Attachments and Call to Arms and ripped em. Would definitely recommend this show as the best of the three night run. However, all three were great.}
\Review{01-21-18}{Beacon Theatre, New York, NY, USA}{Andys\char`_Last\char`_Plunger}{Fuckin' legendary.   I've only been listening to/going to UM shows for about 6 years, so, obviously, I'm fairly new to the band in the grand scheme of things. Also my first time being able to see the band 3 nights in a row, and in my hometown. Friday night was sick, Saturday (my 10th UM show) was somehow even crazier than that, and then we got hit with this.  When they announced the theme at the beginning of the night it opened up a new world of possibilities. Since they limited themselves to playing one debut from each year, the band must have had to go through a lengthy process choosing which songs to play. The setlist that came out of that process reads like a 'Greatest Hits' album (no pun intended). Heavy hitters the entire show, but still with unique moments where you could tell the band was, as they always are, pushing themselves into new territory within their well established material. I've always loved Umphrey's ability to 'rage, rest, repeat' during their shows, they give their audience time to re-energize before hitting their next shot out of the park, but this show was a very, VERY cool change of pace from the band's 'typical' spiel. No rest, no repeats. Only raging.  If you're an Umphrey's McGee fan you absolutely MUST listen to this show. Absolutely fucking incredible.}
\Review{03-07-18}{Belly Up Aspen, Aspen, CO, USA}{drubage}{This show was on fire from the beginning with lots of really fun jams. It seemed like the band was really loose and that they were just really excited to be back on the road together. Opening the show with a Jimmy Stewart is a nice bonus and it really set the tone!}
\Review{08-18-18}{St. Augustine Amphitheatre, St. Augustine, FL, USA}{chrisb}{4th show in 3 years at a great venue. The band really seemed pumped that the house was full and brought the heat! The 'Draconian' opener meandered about for nearly 20 minutes, 'Where is my mind?' surprised and thrilled the crowd, 'Attachments' was amazing and after 10 years I finally caught a 'Nemo'.}
\Review{08-10-19}{Lakefront Green, Chicago, IL, USA}{mscalzo54}{I'm pretty new to UM.  Got into them after seeing the Soundstage video on AXS TV.  So I started watching and listening to them on Music-You Tube and bought a couple of albums on iTunes.  So I'm a mature fan of 65 and I really wanted to see them in concert, so I bought my brother-in-law a ticket so he'd go to the show with me.  Got there early and was almost in the front row.  The music was awesome, although I only recognized 7 of the 17 songs.  The thing that made the concert was when they played Ocean Billy, my favorite UM song in the second set.  I later found out that I could actually buy the concert.  I've been listening to it constantly and am more impressed with it every day.  They are an amazing group.  I was so lucky to hear Hajimemashite, Draconian, Miss Tinkle's Overture to expand my familiarity with UM's songs.  While I originally thought their cover of Layla was OK, listening over and over again...it was a great song to set up Gulf Stream for the finale.  I loved this concert... it was the highlight of my summer.  I will definitely be looking for the opportunity to see UM again.}
